---
title: "BS_Rep_D1"
author: "Beza & Solome"
date: "2023-03-14"
output: pdf_document
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readstata13)
library(ggplot2)
library(reshape2)
library(plyr)
library(margins)
library(descr)
library(sandwich)
library(pscl)
library(psych)
library(effects)
library(multiwayvcov)
library(mirt)
library(moments)
library(haven)
library(datawizard)
library(tidyverse)
library(labelled)
#setting working directory (Beza-- be sure to comments this out and set your own when you are coding!)
knitr::opts_knit$set(root.dir = "/Users/solomonaberash/Desktop/Graduate School/SP23 STATS/Rep Paper/dataverse_files")

#Beza's working directory 
#knitr::opts_knit$set(root.dir = "/Users/bezataddess/Dropbox (Princeton)/Beza$SolomeReplication/Replication.stats")

```


# Data Wrangling

```{r}
##Loading Both Waves of pew_ATP_W64 Data
pew_ATP_W64 <- read_dta("ATP_W64.dta") #this is in haven label type


#subetting relevant portion of wave 64
pew_ATP_W64 <- subset(pew_ATP_W64,
                      select=c(QKEY,COVID_COMFORT_a_W64,COVID_COMFORT_b_W64,
                            COVID_COMFORT_c_W64,COVID_COMFORT_d_W64,COVID_COMFORT_e_W64,
                            COVID_RESTRICTION_a_W64,COVID_RESTRICTION_b_W64,
                            COVID_RESTRICTION_c_W64,COVID_RESTRICTION_d_W64,
                            COVID_RESTRICTION_e_W64,COVID_RESTRICTION_f_W64,
                            COVID_RESTRICTION_g_W64,F_IDEO,F_PARTY_FINAL,F_SEX,
                            F_AGECAT,F_EDUCCAT2,F_MARITAL,F_INCOME,F_CREGION,
                            F_RACETHN,WEIGHT_W64))
```


## Coding and scaling ideological dependent variable (DV) 
## of interest (policy support)
```{r, warning=FALSE}
#subsetting DV data 
covid_ideo_scales <- subset(pew_ATP_W64,
                            select=c(QKEY,COVID_RESTRICTION_a_W64,COVID_RESTRICTION_b_W64,
                                     COVID_RESTRICTION_c_W64,COVID_RESTRICTION_d_W64,
                                     COVID_RESTRICTION_e_W64,COVID_RESTRICTION_f_W64,
                                     COVID_RESTRICTION_g_W64,F_IDEO))

#renaming column names of subsetted data
colnames(covid_ideo_scales) <- c("QKEY","restriction_intl_travel","restriction_most_business",
                                 "restriction_large_gatherings","restriction_sporting_events",
                                 "restriction_closing_k12","restriction_carry_out_only",
                                 "restriction_postponing_primary","libcon")

#transforming observations into characters (had to redone long way, orginal code did not work)
covid_ideo_scales[,2] <- as.character(covid_ideo_scales$restriction_intl_travel)
covid_ideo_scales[,3] <- as.character(covid_ideo_scales$restriction_most_business)
covid_ideo_scales[,4] <- as.character(covid_ideo_scales$restriction_large_gatherings)
covid_ideo_scales[,5] <- as.character(covid_ideo_scales$restriction_sporting_events)
covid_ideo_scales[,6] <- as.character(covid_ideo_scales$restriction_closing_k12)
covid_ideo_scales[,7] <- as.character(covid_ideo_scales$restriction_carry_out_only)
covid_ideo_scales[,8] <- as.character(covid_ideo_scales$restriction_postponing_primary)


#recoding observations into binary --> don't use if else because you don't want to improperly code the incomplete observations that will need to be removed at the end
covid_ideo_scales$restriction_intl_travel <- recode(covid_ideo_scales$restriction_intl_travel, 
                            "1"= 1, "2"= 0)  
covid_ideo_scales$restriction_most_business <- recode(covid_ideo_scales$restriction_most_business, 
                            "1"= 1, "2"= 0) 
covid_ideo_scales$restriction_large_gatherings <- recode(covid_ideo_scales$restriction_large_gatherings, 
                            "1"= 1, "2"= 0)
covid_ideo_scales$restriction_sporting_events <- recode(covid_ideo_scales$restriction_sporting_events, 
                            "1"= 1, "2"= 0) 
covid_ideo_scales$restriction_closing_k12 <- recode(covid_ideo_scales$restriction_closing_k12, 
                            "1"= 1, "2"= 0) 
covid_ideo_scales$restriction_carry_out_only <- recode(covid_ideo_scales$restriction_carry_out_only, 
                            "1"= 1, "2"= 0) 
covid_ideo_scales$restriction_postponing_primary <- recode(covid_ideo_scales$restriction_postponing_primary, 
                            "1"= 1, "2"= 0)

#recoding observations into binary --> this currently (3/17) doesn't work because the variables have not been recorded into necessary/unecessary terms, decided to do the above long/manual way to convert it into a numeric binary 
# covid_ideo_scales[covid_ideo_scales == "Necessary"] <- 1
# covid_ideo_scales[covid_ideo_scales == "Unnecessary"] <- 0

#recoding political ideology variable --> currently (3/17) this yields a bunch of NA's that end up making all the observations 
# covid_ideo_scales$libcon <- ifelse(covid_ideo_scales$libcon %in% "Very Conservative",1,
#                                    ifelse(covid_ideo_scales$libcon %in% "Conservative",2,
#                                           ifelse(covid_ideo_scales$libcon %in% "Moderate",3,
#                                                  ifelse(covid_ideo_scales$libcon %in% "Liberal",4,
#                                                         ifelse(covid_ideo_scales$libcon %in% "Liberal",4,
#                                                                ifelse(covid_ideo_scales$libcon %in% "Very liberal",5,NA))))))

#transforming observations into numeric --> this doesn't work (as of 3/17) and I am not sure it is necessary considering you can just convert the data into a 0/1 numeric binary in one step (as I did in lines 78-91)
# for(i in 2:ncol(covid_ideo_scales)){
#   covid_ideo_scales[,i] <- as.factor(covid_ideo_scales[,i])
# }


#working on the political ideology variable
library(haven)
library(dplyr)

# Convert to regular factor vector
covid_ideo_scales$libcon <- as_factor(covid_ideo_scales$libcon)

# Recode using case_when()
covid_ideo_scales <- covid_ideo_scales %>%
  mutate(
    libcon = case_when(
      libcon == "Very conservative" ~ 1,
      libcon == "Conservative" ~ 2,
      libcon == "Moderate" ~ 3,
      libcon == "Liberal" ~ 4,
      libcon == "Very liberal" ~ 5,
      TRUE ~ NA_real_
    )
  )

# convert back to numeric vector
covid_ideo_scales$libcon <- as.factor(covid_ideo_scales$libcon) 

# converting columns to numeric
covid_ideo_scales[, 2:ncol(covid_ideo_scales)] <- lapply(covid_ideo_scales[, 2:ncol(covid_ideo_scales)], as.factor)

# removing incomplete observations
covid_ideo_scales <- na.omit(covid_ideo_scales)



```


## Factor Analysis (policy support)
```{r}
library(FactoMineR)
library(factoextra)

#transforming observations into factors for factor analysis
x <- covid_ideo_scales[,c(2:9)]
# for(i in 1:8){
#   x[,i] <- as.factor(x[,i])
# }

#trying changing observations into factors the long way
x[,1] <- as.factor(covid_ideo_scales$restriction_intl_travel)
x[,2] <- as.factor(covid_ideo_scales$restriction_most_business)
x[,3] <- as.factor(covid_ideo_scales$restriction_large_gatherings)
x[,4] <- as.factor(covid_ideo_scales$restriction_sporting_events)
x[,5] <- as.factor(covid_ideo_scales$restriction_closing_k12)
x[,6] <- as.factor(covid_ideo_scales$restriction_carry_out_only)
x[,7] <- as.factor(covid_ideo_scales$restriction_postponing_primary)
x[,8] <- as.factor(covid_ideo_scales$libcon)

factanal <- FAMD(x, graph = FALSE,ncp=8,sup.var = NULL)
library(rstatix)

fviz_screeplot(factanal)
fviz_contrib(factanal, "var", axes = 1)
fviz_contrib(factanal, "var", axes = 2)
fviz_contrib(factanal, "var", axes = 3)
fviz_famd_var(factanal, "var", repel = TRUE, col.var = "black")

# Run factor analysis
factanal <- fa(covid_ideo_scales[,c(2:9)], nfactors=2, rotate="promax", fm="pa")
scores <- data.frame(factanal$scores)
loadings(factanal)
loadings <- factanal$loadings
loadings <- data.frame(f1 = loadings[,1],f2=loadings[,2])

plot(factanal$loadings,type="n") # set up plot 
text(factanal$loadings,labels=names(covid_ideo_scales)[2:9],cex=.7) # add variable names
#gh
library(ggrepel)

alpha(covid_ideo_scales[,c(2:9)])

library(grid)
library(gridExtra)
loadings$vars <- ifelse(rownames(loadings) %in% "restriction_intl_travel","International Travel",
                        ifelse(rownames(loadings) %in% "restriction_most_business","Most Businesses",
                               ifelse(rownames(loadings) %in% "restriction_large_gatherings","Large Gatherings",
                                      ifelse(rownames(loadings) %in% "restriction_sporting_events","Sporting Events",
                                             ifelse(rownames(loadings) %in% "restriction_closing_k12","K-12 Schools",
                                                    ifelse(rownames(loadings) %in% "restriction_carry_out_only","Carry-out Only",
                                                           ifelse(rownames(loadings) %in% "restriction_postponing_primary","Postponing Primary",
                                                                  ifelse(rownames(loadings) %in% "libcon","Left-Right Ideology",NA))))))))

#plotting factor analysis plot
plot <- ggplot(loadings,aes(x = f1, y=f2,label=vars)) + 
  theme_minimal() + 
  geom_label_repel() + 
  scale_x_continuous("First Dimension Factor (Proportion of Variance: 36%)") + 
  scale_y_continuous("Second Dimension Factor (Propoportion of Variance 4%)") + 
  geom_segment(aes(x = 0,y = 0,xend = f1,yend = f2),arrow=arrow()) 

grid.newpage()
footnote <- expression("Cronbach's Standardized"~alpha~"="~0.78)
g <- arrangeGrob(plot, 
                 bottom = textGrob(footnote, x = 0.025, hjust = 0, vjust= 0, 
                                   y=0.75, gp = gpar(fontface = "italic", 
                                                     fontsize = 9, col = "black")))
grid.draw(g)
ggsave(file="factor_analysis_covid19_policies.png", g, width = 8, height = 5.43, units = "in")

covid_ideo_scales <- cbind(covid_ideo_scales,scores)
colnames(covid_ideo_scales)[10:11] <- c("covid_restriction_fa_dim1","covid_restriction_fa_dim2")
covid_ideo_scales$summated_restriction_scale <- rowSums(covid_ideo_scales[2:8],na.rm=T)
```


## Item-Response Theory Model= "The item response theory (IRT), also known as the latent response theory refers to a family of mathematical models that attempt to explain the relationship between latent traits (unobservable characteristic or attribute) and their manifestations (i.e. observed outcomes, responses or performance). They establish a link between the properties of items on an instrument, individuals responding to these items and the underlying trait being measured. IRT assumes that the latent construct (e.g. stress, knowledge, attitudes) and items of a measure are organized in an unobservable continuum. Therefore, its main purpose focuses on establishing the individual’s position on that continuum."

## In this context, IRT is used to create a continuum with the various COVID policy questions and the aggregate score of a respondant's answers to the questions will proxy as an overall measure of support (which is a latent variable) for social distancing policies

**NOTE: this whole chunk works but I want to know the more granular mechanics of how/why, but leave that to me**
```{r}
irt <- mirt(covid_ideo_scales[2:8], model = 1, itemtype = "graded", SE = T, 
            verbose = T,removeEmptyRows = TRUE)

plt <- plot(irt, type = 'trace', facet_items=F) #store the object
print(plt) #plot the object
#str(plt) #find the data
pltdata <- data.frame(lapply(plt$panel.args, function(x) do.call(cbind, x))[[1]])

groups <- plot(irt, type = 'trace', facet_items=T)
#groups$packet.sizes
pltdata$item <- rep(colnames(covid_ideo_scales)[2:8], each = 200)
pltdata$response <- groups$panel.args.common$groups

#plt$panel.args.common$groups

pltdata$item2 <- factor(pltdata$item,levels=c("restriction_carry_out_only",
                                              "restriction_closing_k12",
                                              "restriction_intl_travel",
                                              "restriction_large_gatherings",
                                              "restriction_most_business",
                                              "restriction_postponing_primary",
                                              "restriction_sporting_events"),
                        labels=c("Carry Out Only","Close K-12 Schools",
                                 "Restrict Intl. Travel","Restrict Large Gatherings",
                                 "Restrict Most Businesses","Postpone Primary Elections",
                                 "Restrict Sporting Events"))

pltdata$item2 <- factor(pltdata$item2,levels=c("Restrict Intl. Travel",
                                               "Restrict Sporting Events",
                                               "Close K-12 Schools",
                                               "Restrict Large Gatherings",
                                               "Carry Out Only","Restrict Most Businesses",
                                               "Postpone Primary Elections"))

plot <- ggplot(pltdata, aes(x, y,linetype=item2,color=item2)) + 
  geom_line() + 
  scale_x_continuous(expression(theta)) + 
  scale_y_continuous("Pr (Support)") + 
  geom_hline(aes(yintercept = 0.5))  + 
  theme_minimal() + 
  labs(color="Policy",linetype="Policy") + 
  theme(legend.position="bottom")
#+ scale_colour_grey(start = 0, end = .5) + 
#  ggtitle("Ordinal IRT Model Characteric Curves for Emphatic Racism Scale")

#ggsave(file="covid19_restrictions_irt_curves_probs.png", plot, width = 8, height = 5.43, units = "in")
```

## Scores= the scores generated from the IRT continuum for each of the respondants (this is the ultimate support for social distancing policy that serves as the DV)

**whole thing runs!: March 22**
```{r}
#storing scores from IRT analysis for each respondent in original covid scales data
covid_ideo_scales$covid_restriction_fa_dim2 <- fscores(irt, full.scores = TRUE, full.scores.SE = F)
colnames(covid_ideo_scales)[11] <- "covid_restriction_irt"

# colnames(covid_ideo_scales)
# colnames(pew_ATP_W64)

#merging with original data set 
pew_ATP_W64 <- merge(pew_ATP_W64,covid_ideo_scales,by=c("QKEY"),all=T)

pew_ATP_W64$covid_restriction_fa_dim1 <- pew_ATP_W64$covid_restriction_fa_dim1- mean(pew_ATP_W64$covid_restriction_fa_dim1,na.rm=T)
```

## Covariates

**whole thing runs!**
```{r}
#transforming gender covariate & plotting
pew_ATP_W64$female <- as.character(pew_ATP_W64$F_SEX)
pew_ATP_W64$female <- recode(pew_ATP_W64$female, "1" = "Male", "2"= "Female")
pew_ATP_W64$female <- factor(pew_ATP_W64$female,levels=c("Male","Female"))

df_64 <- as.data.frame(cbind(pew_ATP_W64$female, pew_ATP_W64$covid_restriction_fa_dim1))

ggplot(data= na.omit(df_64),
       aes(x=as.factor(V1),y= V2)) + geom_boxplot() + 
  labs(title = "Boxplot of Sex Covariate of Wave 64",
       x= "Sex (Male=1, Female=2)",
       y= "covid_restriction_fa_dim1")

#transforming political identification & using to create weights
pew_ATP_W64$pid3 <- as.character(pew_ATP_W64$F_PARTY_FINAL)
pew_ATP_W64$pid3 <- factor(pew_ATP_W64$pid3,levels=c("Republican","Independent","Democrat"))

pew_ATP_W64$weight <- as.factor(pew_ATP_W64$WEIGHT_W64)

#transforming & cleaning age covariate
pew_ATP_W64$age_linear <- as.factor(factor(pew_ATP_W64$F_AGECAT))
pew_ATP_W64$age_linear[pew_ATP_W64$age_linear %in% 5] <- NA # Get rid of refused

#transforming & cleaning education covariate
pew_ATP_W64$educ_linear <- as.factor(factor(pew_ATP_W64$F_EDUCCAT2))
pew_ATP_W64$educ_linear[pew_ATP_W64$educ_linear %in% 7] <- NA # Get rid of refused

#transforming & cleaning marital covariate
pew_ATP_W64$marital_status <- ifelse(pew_ATP_W64$F_MARITAL %in% "Married",1,0)
pew_ATP_W64$marital_status[pew_ATP_W64$F_MARITAL %in% "Refused"] <- NA # Get rid of refused

#transforming & cleaning income covariate
pew_ATP_W64$income_linear <- as.factor(factor(pew_ATP_W64$F_INCOME))
pew_ATP_W64$income_linear[pew_ATP_W64$income_linear %in% 10] <- NA # Get rid of refused

#transforming & cleaning region & white race covariates
pew_ATP_W64$region_factor <- pew_ATP_W64$F_CREGION
pew_ATP_W64$white_respondent <- ifelse(pew_ATP_W64$F_RACETHN %in% "White non-Hispanic",1,0)
pew_ATP_W64$white_respondent[pew_ATP_W64$F_RACETHN %in% "Refused"] <- NA # Get rid of refused

#getting other race covariate
hold <- read_dta("ATP_W42.dta")
hold <- hold[,c("QKEY", "F_RACECMB")]

pew_ATP_W64 <- merge(pew_ATP_W64,hold,by=c("QKEY"),all=T)

pew_ATP_W64$race3 <- ifelse(pew_ATP_W64$F_RACETHN %in% "White non-Hispanic","white",ifelse(pew_ATP_W64$F_RACETHN %in% "Black non-Hispanic","black",ifelse(pew_ATP_W64$F_RACETHN %in% "Hispanic","hispanic",NA)))
pew_ATP_W64$race3 <- ifelse(is.na(pew_ATP_W64$race3) & pew_ATP_W64$F_RACECMB %in% "Asian or Asian-American","asian",pew_ATP_W64$race3)

pew_ATP_W64$race3 <- factor(pew_ATP_W64$race3,levels=c("white","black","hispanic","asian"))
```



## Trust
```{r}
#loading trust data from wave 42
trust <- read_dta("ATP_W42.dta")
trust <- subset(trust,select=c("QKEY","CONFa_W42","CONFb_W42","CONFd_F1_W42",
                               "CONFd_F2_W42", "POLICY1_W42","POLICY2_W42",
                               "POLICY3_W42","SCM2_W42","SCM3_W42","SCM4a_W42",
                               "SCM4b_W42"))
str(trust)

colnames(trust) <- c("QKEY","trust_elected_officials","trust_media",
                     "trust_medial_scientists","trust_scientists",
                     "scientists_active_role_policy","scientists_pivotal_policy",
                     "scientists_better_policy","scientific_method",
                     "scientists_judgement_facts","research_essential_immediate_applications",
                     "research_essential_advance_knowledge")


#recoding into character because loops below didn't work
trust$trust_elected_officials <- as.character(trust$trust_elected_officials)
trust$trust_media <- as.character(trust$trust_media)
trust$trust_medial_scientists <- as.character(trust$trust_medial_scientists)
trust$trust_scientists <- as.character(trust$trust_scientists)
trust$scientists_active_role_policy <- as.character(trust$scientists_active_role_policy)
trust$scientists_pivotal_policy <- as.character(trust$scientists_pivotal_policy)
trust$scientists_better_policy <- as.character(trust$scientists_better_policy)
trust$scientific_method <- as.character(trust$scientific_method)
trust$scientists_judgement_facts <- as.character(trust$scientists_judgement_facts )
trust$research_essential_immediate_applications <- as.character(trust$research_essential_immediate_applications)
trust$research_essential_advance_knowledge <- as.character(trust$research_essential_advance_knowledge)

#omitting non-responses # this doesn't work because it's already coded as NA, but "refused"
#trust[trust$trust_elected_officials == "Refused"] <- NA 


# #adding levels
# for(i in 2:ncol(trust)){
#   print(table(trust[,i]))
#   print(trust[,i])
# }
# for(i in 2:ncol(trust)){
#   trust[,i] <- as.character(trust[,i])
#   print(trust[,i])
# }

#omitting non-responses 
trust[trust == "Refused"] <- NA 

#recoding responses to each trust survey question 
trust[trust == "Essential"] <- 4
trust[trust == "Important, but not essential"] <- 3
trust[trust == "Not too important"] <- 2
trust[trust == "Not important at all"] <- 1

trust[trust == "A great deal of confidence"] <- 4
trust[trust == "A fair amount of confidence"] <- 3
trust[trust == "Not too much confidence"] <- 2
trust[trust == "No confidence at all"] <- 1

trust[trust == "Scientists should take an active role in public policy debates about scientific issues"] <- 2
trust[trust == "Scientists should focus on establishing sound scientific facts and stay out of public policy debates"] <- 1

trust[trust == "Public opinion should NOT play an important role to guide policy decisions about scientific issues because these issues"] <- 2
trust[trust == "Public opinion should play an important role to guide policy decisions about scientific issues"] <- 1

trust[trust == "Usually BETTER at making good policy decisions about scientific issues than other people"] <- 3
trust[trust == "NEITHER BETTER NOR WORSE at making good policy decisions about scientific issues than other people"] <- 2
trust[trust == "Usually WORSE at making good policy decisions about scientific issues than other people"] <- 1

trust[trust == "The scientific method generally produces accurate conclusions"] <- 2
trust[trust == "The scientific method can be used to produce any conclusion the researcher wants"] <- 1

trust[trust == "Scientists make judgments based solely on the facts"] <- 2
trust[trust == "Scientists' judgments are just as likely to be biased as other people's"] <- 1

#indicating incomplete observations as NA
trust$trust_scientists <- ifelse(is.na(trust$trust_medial_scientists),trust$trust_scientists,
                                 ifelse(is.na(trust$trust_scientists),trust$trust_medial_scientists,NA))

trust$trust_medial_scientists <- NULL
trust$scientists_pivotal_policy <- NULL



for(i in 2:ncol(trust)){
  trust[,i] <- as.numeric(trust[,i])
  print(table(trust[,i]))


#recoding maually into factor because loop above did not work
trust$trust_elected_officials <- as.factor(trust$trust_elected_officials)
trust$trust_media <- as.factor(trust$trust_media)
#trust$trust_medial_scientists <- as.factor(trust$trust_medial_scientists)
trust$trust_scientists <- as.factor(trust$trust_scientists)
trust$scientists_active_role_policy <- as.factor(trust$scientists_active_role_policy)
#trust$scientists_pivotal_policy <- as.factor(trust$scientists_pivotal_policy)
trust$scientists_better_policy <- as.factor(trust$scientists_better_policy)
trust$scientific_method <- as.factor(trust$scientific_method)
trust$scientists_judgement_facts <- as.factor(trust$scientists_judgement_facts )
trust$research_essential_immediate_applications <- as.factor(trust$research_essential_immediate_applications)
trust$research_essential_advance_knowledge <- as.factor(trust$research_essential_advance_knowledge)


#recoding into numeric
# for(i in 2:ncol(trust)){
#   trust[,i] <- as.numeric(trust[,i])
#   print(table(trust[,i]))
# } 

#recoding maually into numeric because loop above did not work
trust$trust_elected_officials <- as.numeric(trust$trust_elected_officials)
trust$trust_media <- as.numeric(trust$trust_media)
#trust$trust_medial_scientists <- as.numeric(trust$trust_medial_scientists)
trust$trust_scientists <- as.numeric(trust$trust_scientists)
trust$scientists_active_role_policy <- as.numeric(trust$scientists_active_role_policy)
#trust$scientists_pivotal_policy <- as.numeric(trust$scientists_pivotal_policy)
trust$scientists_better_policy <- as.numeric(trust$scientists_better_policy)
trust$scientific_method <- as.numeric(trust$scientific_method)
trust$scientists_judgement_facts <- as.numeric(trust$scientists_judgement_facts )
trust$research_essential_immediate_applications <- as.numeric(trust$research_essential_immediate_applications)
trust$research_essential_advance_knowledge <- as.numeric(trust$research_essential_advance_knowledge)


#conducting factor analysis to generate factor analysis plots
factanal <- fa(trust[,c(4:10)], nfactors=2, rotate="promax", fm="pa")
scores <- data.frame(factanal$scores)
loadings(factanal)
loadings <- factanal$loadings
loadings <- data.frame(f1 = loadings[,1],f2=loadings[,2])

plot(factanal$loadings,type="n") # set up plot 
text(factanal$loadings,labels=names(trust)[4:10],cex=.7) # add variable names

library(ggrepel)

alpha(trust[,c(4:8)])
skewness(loadings$f1, na.rm=T)
kurtosis(loadings$f1, na.rm=T)

alpha(trust[,c(9:10)])
skewness(loadings$f2, na.rm=T)
kurtosis(loadings$f2, na.rm=T)

loadings$vars <- ifelse(rownames(loadings) %in% "trust_scientists","Trust Scientists",ifelse(rownames(loadings) %in% "scientists_active_role_policy","Scientists Active Role Policy",ifelse(rownames(loadings) %in% "scientists_pivotal_policy","PO Guiding Policy Science",ifelse(rownames(loadings) %in% "scientists_better_policy","Scientists Better Policymakers",ifelse(rownames(loadings) %in% "scientific_method","Scientific Method Validity",ifelse(rownames(loadings) %in% "scientists_judgement_facts","Unbiased Scientists",ifelse(rownames(loadings) %in% "research_essential_immediate_applications","Research Essential Applications",ifelse(rownames(loadings) %in% "research_essential_advance_knowledge","Research Essential Knowledge",NA))))))))

plot <- ggplot(loadings,aes(x = f1, y=f2,label=vars)) + theme_minimal() + geom_label_repel() + scale_x_continuous("First Dimension Factor") + scale_y_continuous("Second Dimension Factor") + geom_segment(aes(x = 0,y = 0,xend = f1,yend = f2),arrow=arrow())  # (Proportion of Variance F1: 18%) (Propoportion of F2 Variance 16%)"
library(grid)
grid.newpage()

footnote <- expression("Cronbach's Standardized"~alpha~"="~0.66)

library(gridExtra)
g <- arrangeGrob(plot, bottom = textGrob(footnote, x = 0.025, hjust = 0, vjust= 0, y=0.75, gp = gpar(fontface = "italic", fontsize = 9, col = "black")))
grid.draw(g)
#ggsave(file="factor_analysis_scientific_trust.png", g, width = 8, height = 5.43, units = "in")

trust <- cbind(trust,scores)
colnames(trust)[11:12] <- c("trust_scientists_fa_dim1","trust_scientists_fa_dim2")

pew_ATP_W64 <- merge(pew_ATP_W64,trust,by=c("QKEY"),all=T)

x0 <- subset(pew_ATP_W64,select=c(pid3,trust_scientists_fa_dim1,trust_scientists_fa_dim2))
x0 <- na.omit(x0)
x0$pid <- ifelse(x0$pid3 %in% "Democrat","D",ifelse(x0$pid3 %in% "Republican","R",ifelse(x0$pid3 %in% "Independent","I",NA)))

plot <- ggplot(x0,aes(x=trust_scientists_fa_dim1,y=trust_scientists_fa_dim2,label=pid,color=pid)) + geom_text(alpha=0.2) + scale_color_manual("",values=c("blue","purple","red"))

x1 <- x0
x1$pid3 <- "Full Sample"
x_ <- rbind(x0,x1)
x_$pid3 <- factor(x_$pid3,levels=c("Republican","Independent","Democrat","Full Sample"),labels=c("Republican Partisans","Independent Partisans","Democratic Partisans","Full Sample"))

print(summary(aov(trust_scientists_fa_dim1 ~ pid3, data = x_)))

plot <- ggplot(x_, aes(x=pid3,y=trust_scientists_fa_dim1, group=pid3,fill=pid3)) + geom_boxplot(alpha=0.2) + theme_minimal() + scale_y_continuous("Latent Scientific Trust") + scale_x_discrete("") + scale_fill_manual("",values=c("red","purple","blue","black")) + theme(legend.position = "none") 
#ggsave(file="scientific_trust_boxplots_by_party.png", plot, width = 8, height = 5.43, units = "in")
```

# Data Analysis: COVID Policy ~ Scientific Trust: Baseline Effects

## Baseline Trust Effects
```{r, eval=FALSE}
baseline_trust_effects <- list()
for(i in which(colnames(pew_ATP_W64) == "restriction_intl_travel"):which(colnames(pew_ATP_W64) == "restriction_postponing_primary")){
  summary(model <- glm(pew_ATP_W64[,i] ~ trust_scientists_fa_dim1 + trust_media + trust_elected_officials + female + pid3 + libcon + age_linear + educ_linear + income_linear + race3 + region_factor, data=pew_ATP_W64, weights=weight, family = binomial(link = "logit")))
  mes <- summary(margins(model, variables=c("trust_scientists_fa_dim1","trust_media","trust_elected_officials"), type="response", change="minmax"))
  mes$model <- colnames(pew_ATP_W64)[i]
  mes$category <- "Full Sample Baseline"
  baseline_trust_effects[[i]] <- mes
}
baseline_trust_effects <- ldply(baseline_trust_effects,data.frame)

baseline_trust_effects$pid3 <- "Full Baseline Sample"
baseline_trust_effects$category <- NULL

effects <- baseline_trust_effects
effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))
effects$model2 <- ifelse(effects$model %in% "restriction_carry_out_only","Dependent Variable: Restaurants Carry Out Only",
                         ifelse(effects$model %in% "restriction_closing_k12","Dependent Variable: Close K-12 Schools",
                                ifelse(effects$model %in% "restriction_intl_travel","Dependent Variable: Restrict International Travel",
                                       ifelse(effects$model %in% "restriction_large_gatherings","Dependent Variable: Restrict Large Gatherings",
                                              ifelse(effects$model %in% "restriction_most_business","Dependent Variable: Restrict Most Businesses",
                                                     ifelse(effects$model %in% "restriction_postponing_primary","Dependent Variable: Postpone Primary Elections",
                                                            ifelse(effects$model %in% "restriction_sporting_events","Dependent Variable: Restrict Sporting Events",NA)))))))

effects$factor <- ifelse(effects$factor %in% "trust_elected_officials","Elected Officials Trust",
                         ifelse(effects$factor %in% "trust_media","Media Trust",
                                ifelse(effects$factor %in% "trust_scientists_fa_dim1","Scientific Trust",NA)))

effects$label <- ifelse(effects$p < 0.01,paste(round(effects$AME,2),"***",sep=""),
                        ifelse(effects$p < 0.05,paste(round(effects$AME,2),"**",sep=""),
                               ifelse(effects$p < 0.10,paste(round(effects$AME,2),"*",sep=""),NA)))


for(i in unique(effects$model)){
  x <- subset(effects,effects$model %in% i)
  plot <- ggplot(x,aes(x=factor,y=AME,factor=factor,group=factor,color=factor,shape=factor,label=label,fill=factor)) + 
    facet_wrap(~model2) + coord_flip() + 
    geom_linerange(aes(x= factor, ymin = ylo90, ymax = yhi90), position = position_dodge(width=0.75), lwd  = 1) + 
    geom_pointrange(aes(x= factor, ymin = lower, ymax = upper), lwd = 1/2, position = position_dodge(width=0.75),fill="white") + 
    theme_minimal() + scale_x_discrete("") + scale_y_continuous("Min/Max First Difference Marginal Effects on Pr(Necessary Government Policy)") + 
    geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  
    labs(color="Trust Effects",shape="Trust Effects") + 
    theme(legend.position = "none") + 
    theme(axis.text.x = element_text(hjust = 0.5),axis.text.y = element_text(hjust = 0.5)) + 
    geom_label(vjust=-0.5,hjust=0.25,fill="white") + labs(caption="* p < 0.1; ** p < 0.05; *** p < 0.01") + 
    scale_shape_manual("",values=c(23,22,21))
  print(plot)
  #ggsave(file=paste(i,"_model",".png",sep=""), plot, width = 8, height = 5.43, units = "in")
}
```


## Distribution of Summated Rating Scales
```{r, eval=F}
x <- subset(pew_ATP_W64,select=c(summated_restriction_scale,trust_scientists_fa_dim1,pid3,trust_media,trust_elected_officials,female,libcon,age_linear,educ_linear,income_linear,white_respondent,region_factor,race3))
x1 <- na.omit(x)
x <- na.omit(x)
x1$race3 <- "Full Sample"

x <- subset(x,select=c(summated_restriction_scale,race3))
x$n <- 1
xs <- ddply(x,.(summated_restriction_scale,race3),summarise,total=sum(n,na.rm=T))
x <- ddply(x,.(race3),summarise,total_race3=sum(n,na.rm=T))
xs <- merge(xs,x,by=c("race3"))
xs$prop <- xs$total/xs$total_race3

x1 <- subset(x1,select=c(summated_restriction_scale,race3))
x1$n <- 1
xs1 <- ddply(x1,.(summated_restriction_scale),summarise,total=sum(n,na.rm=T))
xs1$total_race3 <- sum(x1$n,na.rm=T)
xs1$prop <- xs1$total/xs1$total_race3
xs1$race3 <- "Full Sample"

x <- rbind(xs,xs1)
x$race3 <- factor(x$race3,levels=c("asian","black","hispanic","white","Full Sample"),labels=c("Asian Respondents","Black Respondents","Hispanic Respondents","White Respondents","Full Sample"))

plot <- ggplot(x, aes(x=factor(summated_restriction_scale), y=prop, label=round(prop,2))) + geom_point(stat='identity', size=6*1.25) + geom_segment(aes(y=0,x=factor(summated_restriction_scale),yend=prop,xend=factor(summated_restriction_scale)))+ geom_text(color="white", size=2*1.25) + coord_flip() + facet_wrap(~race3) + theme_minimal() + theme(legend.position = "none") + scale_x_discrete("Number of Restrictive COVID-19 Policies Necessary") + scale_y_continuous("Proportion of Respondents")
#ggsave(file="number_policies_dotplot.png", plot, width = 8, height = 5.43, units = "in")
```


# Conditioned by Race
# Data Analysis: COVID Policy ~ Scientific Trust: Baseline Effects

## Baseline Trust Effects
```{r, eval=F}
baseline_trust_effects.race <- list()
for(i in which(colnames(pew_ATP_W64) == "restriction_intl_travel"):which(colnames(pew_ATP_W64) == "restriction_postponing_primary")){
  summary(model <- glm(pew_ATP_W64[,i] ~ trust_scientists_fa_dim1*race3 + trust_media + trust_elected_officials + female + pid3 + libcon + age_linear + educ_linear + income_linear + region_factor, data=pew_ATP_W64, weights=weight, family = binomial(link = "logit")))
  mes <- summary(margins(model, variables=c("trust_scientists_fa_dim1","trust_media","trust_elected_officials"),at=list(race3=c("asian","black","white","hispanic")), type="response", change="minmax",))
  mes$model <- colnames(pew_ATP_W64)[i]
  mes$category <- "Full Sample Baseline"
  baseline_trust_effects.race[[i]] <- mes
}
baseline_trust_effects.race <- ldply(baseline_trust_effects.race,data.frame)


effects <- baseline_trust_effects.race
effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))
effects$model2 <- ifelse(effects$model %in% "restriction_carry_out_only","Dependent Variable: Restaurants Carry Out Only",ifelse(effects$model %in% "restriction_closing_k12","Dependent Variable: Close K-12 Schools",ifelse(effects$model %in% "restriction_intl_travel","Dependent Variable: Restrict International Travel",ifelse(effects$model %in% "restriction_large_gatherings","Dependent Variable: Restrict Large Gatherings",ifelse(effects$model %in% "restriction_most_business","Dependent Variable: Restrict Most Businesses",ifelse(effects$model %in% "restriction_postponing_primary","Dependent Variable: Postpone Primary Elections",ifelse(effects$model %in% "restriction_sporting_events","Dependent Variable: Restrict Sporting Events",NA)))))))
effects$factor <- ifelse(effects$factor %in% "trust_elected_officials","Elected Officials Trust",ifelse(effects$factor %in% "trust_media","Media Trust",ifelse(effects$factor %in% "trust_scientists_fa_dim1","Scientific Trust",NA)))
effects$race3 <- factor(effects$race3,levels=c("asian","black","white","hispanic"), labels=c("Asian Respondents","Black Respondents","White Respondents","Hispanic Respondents"))

for(i in unique(effects$model)){
  x <- subset(effects,effects$model %in% i)
  plot <- ggplot(x,aes(x=race3,y=AME,factor=factor,group=factor,color=factor,shape=factor)) + facet_wrap(~model2) + coord_flip() + geom_linerange(aes(x= race3, ymin = ylo90, ymax = yhi90), position = position_dodge(width=0.75), lwd  = 1) + geom_pointrange(aes(x= race3, ymin = lower, ymax = upper), lwd = 1/2, position = position_dodge(width=0.75),fill="white") + theme_minimal() + scale_x_discrete("") + scale_y_continuous("Min/Max First Difference Marginal Effects on Pr(Necessary Government Policy)") + geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  labs(color="Trust Effects",shape="Trust Effects") + theme(legend.position = "bottom") + theme(axis.text.x = element_text(hjust = 0.5),axis.text.y = element_text(hjust = 0.5)) + scale_shape_manual("Trust Effects",values=c(23,22,21))
  print(plot)
  #ggsave(file=paste(i,"_race3_model",".png",sep=""), plot, width = 8, height = 5.43, units = "in")
}

```


# Data Analysis Figures: OLS Composite Models
```{r, eval=F}
summary(model <- glm(covid_restriction_irt ~ trust_scientists_fa_dim1*race3 + trust_media*race3 + trust_elected_officials*race3 + female + libcon + age_linear + educ_linear + income_linear + region_factor, data=pew_ATP_W64, weights=weight, family = gaussian(identity)))
baseline_trust_effects.4 <- summary(margins(model, variables=c("trust_scientists_fa_dim1","trust_media","trust_elected_officials"),at=list(race3=c("asian","white","black","hispanic")), type="response", change="minmax"))
baseline_trust_effects.4$model <- "DV: Latent Policy Scale"
baseline_trust_effects.4$pid3 <- "Full Sample"

effects <- baseline_trust_effects.4
effects$race3 <- factor(effects$race3,levels=c("asian","black","white","hispanic"), labels=c("Asian Respondents","Black Respondents","White Respondents","Hispanic Respondents"))

effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))

effects$factor <- ifelse(effects$factor %in% "trust_elected_officials","Elected Officials Trust",ifelse(effects$factor %in% "trust_media","Media Trust",ifelse(effects$factor %in% "trust_scientists_fa_dim1","Scientific Trust",NA)))

plot <- ggplot(effects,aes(x=race3,y=AME,factor=factor,group=factor,color=factor,shape=factor)) + facet_wrap(~model) + coord_flip() + geom_linerange(aes(x= race3, ymin = ylo90, ymax = yhi90), position = position_dodge(width=0.75), lwd  = 1) + geom_pointrange(aes(x= race3, ymin = lower, ymax = upper), lwd = 1/2, position = position_dodge(width=0.75),fill="white") + theme_minimal() + scale_x_discrete("") + scale_y_continuous("Min/Max First Difference Marginal Effects on Latent Policy Restriction Scale") + geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  labs(color="Trust Effects",shape="Trust Effects") + theme(legend.position = "bottom") + theme(axis.text.x = element_text(hjust = 0.5),axis.text.y = element_text(hjust = 0.5)) + scale_shape_manual("Trust Effects",values=c(23,22,21))
print(plot)
#ggsave(file="latent_policy_scale_race3_model.png", plot, width = 8, height = 5.43, units = "in")

summary(model <- glm(summated_restriction_scale ~ trust_scientists_fa_dim1*race3 + trust_media*race3 + trust_elected_officials*race3 + female + libcon + age_linear + educ_linear + income_linear + region_factor, data=pew_ATP_W64, weights=weight, family = gaussian(identity)))
baseline_trust_effects.5 <- summary(margins(model, variables=c("trust_scientists_fa_dim1","trust_media","trust_elected_officials"),at=list(race3=c("asian","white","black","hispanic")), type="response", change="minmax"))
baseline_trust_effects.5$model <- "DV: Summated Policy Scale"
baseline_trust_effects.5$pid3 <- "Full Sample"

effects <- baseline_trust_effects.5
effects$race3 <- factor(effects$race3,levels=c("asian","black","white","hispanic"), labels=c("Asian Respondents","Black Respondents","White Respondents","Hispanic Respondents"))

effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))

effects$factor <- ifelse(effects$factor %in% "trust_elected_officials","Elected Officials Trust",ifelse(effects$factor %in% "trust_media","Media Trust",ifelse(effects$factor %in% "trust_scientists_fa_dim1","Scientific Trust",NA)))

plot <- ggplot(effects,aes(x=race3,y=AME,factor=factor,group=factor,color=factor,shape=factor)) + facet_wrap(~model) + coord_flip() + geom_linerange(aes(x= race3, ymin = ylo90, ymax = yhi90), position = position_dodge(width=0.75), lwd  = 1) + geom_pointrange(aes(x= race3, ymin = lower, ymax = upper), lwd = 1/2, position = position_dodge(width=0.75),fill="white") + theme_minimal() + scale_x_discrete("") + scale_y_continuous("Min/Max First Difference Marginal Effects on Number of Necessary Government Policies") + geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  labs(color="Trust Effects",shape="Trust Effects") + theme(legend.position = "bottom") + theme(axis.text.x = element_text(hjust = 0.5),axis.text.y = element_text(hjust = 0.5)) + scale_shape_manual("Trust Effects",values=c(23,22,21))
print(plot)
#ggsave(file="summated_policy_scale_race3_model.png", plot, width = 8, height = 5.43, units = "in")
```


## Boxplot by Race
```{r, eval=F}
x <- subset(pew_ATP_W64,select=c(race3,trust_scientists_fa_dim1))
x <- na.omit(x)
print(summary(aov(trust_scientists_fa_dim1 ~ race3, data = x)))
y <- subset(pew_ATP_W64,select=c(race3,trust_scientists_fa_dim1))
y$race3 <- "Full Sample"
x <- rbind(x,y)

plot <- ggplot(x, aes(x=race3,y=trust_scientists_fa_dim1, group=race3,fill=race3)) + geom_boxplot(alpha=0.2) + theme_minimal() + scale_y_continuous("Latent Scientific Trust") + scale_x_discrete("",labels=c("White Respondents","Black Respondents","Hispanic Respondents","Asian Respondents","Full Sample")) + theme(legend.position = "none") + labs(caption="ANOVA suggests significant differences in mean latent scientific trust across racial groups, p < 0.01.") + geom_jitter(aes(colour=race3),alpha=0.075) + scale_color_manual("",values=c("#F8766D","#7CAE00","#00BFC4","#529EFF","gray")) + scale_fill_manual("",values=c("#F8766D","#7CAE00","#00BFC4","#529EFF","gray"))
#ggsave(file="scientific_trust_boxplots_by_race3.png", plot, width = 8, height = 5.43, units = "in")
```

# Data Analysis Figures: OLS Composite Models
```{r, eval=F}
summary(model <- lm(trust_scientists_fa_dim1 ~ female + pid3 + libcon + age_linear + educ_linear + income_linear + race3 + region_factor, data=pew_ATP_W64, weights=weight))

mes <- summary(margins(model, type="response", change="minmax"))
mes$race3 <- factor(mes$factor,levels=c("race3asian","race3black","race3hispanic"),labels=c("Asian Respondents","Black Respondents","Hispanic Respondents"))

mes$label <- ifelse(mes$p < 0.01,paste(round(mes$AME,2),"***",sep=""),ifelse(mes$p < 0.05,paste(round(mes$AME,2),"**",sep=""),ifelse(mes$p < 0.10,paste(round(mes$AME,2),"*",sep=""),NA)))

mes$ylo90 <- (mes$AME - (qt(.95, 100) * mes$SE))
mes$yhi90 <- (mes$AME + (qt(.95, 100) * mes$SE))
mes$model <- "DV: Latent Scientific Trust "

plot <- ggplot(subset(mes,!is.na(mes$race3)),aes(x=race3,y=AME,factor=race3,group=race3,color=race3,shape=race3,label=label,fill=race3)) + facet_wrap(~model) + coord_flip() + geom_linerange(aes(x= race3, ymin = ylo90, ymax = yhi90), position = position_dodge(width=0.75), lwd  = 1) + geom_pointrange(aes(x= race3, ymin = lower, ymax = upper), lwd = 1/2, position = position_dodge(width=0.75),fill="white") + theme_minimal() + scale_x_discrete("") + scale_y_continuous("Marginal Effect of Race on Latent Scientific Trust")  + geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  labs(color="Trust Effects",shape="Trust Effects") + theme(legend.position = "none") + theme(axis.text.x = element_text(hjust = 0.5),axis.text.y = element_text(hjust = 0.5)) + geom_label(vjust=-0.5,hjust=0.25,fill="white") + labs(caption="Note marginal effects relative to white respondents. \n* p < 0.1; ** p < 0.05; *** p < 0.01") + facet_wrap(~model) + scale_shape_manual("Trust Effects",values=c(23,22,21))
ggsave(file="latent_scientific_trust_model.png", plot, width = 8, height = 5.43, units = "in")

mes <- subset(mes,!(mes$factor %in% c("region_factorWest","region_factorSouth","region_factorMidwest")))

plot <- ggplot(mes,aes(x=factor,y=AME,factor=factor,group=factor,label=label)) + facet_wrap(~model) + coord_flip() + geom_linerange(aes(x= factor, ymin = ylo90, ymax = yhi90), position = position_dodge(width=0.75), lwd  = 1) + geom_pointrange(aes(x= factor, ymin = lower, ymax = upper), lwd = 1/2, position = position_dodge(width=0.75),fill="white",shape=21) + theme_minimal() + scale_x_discrete("",labels=c("Age","Education","Female","Income","Liberal Ideology","Democrat","Independent","Asian Respondent","Black Respondent","Hispanic Respondent")) + scale_y_continuous("Marginal Effect of Covariates on Latent Scientific Trust")  + geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  labs(color="Trust Effects",shape="Trust Effects") + theme(legend.position = "none") + theme(axis.text.x = element_text(hjust = 0.5),axis.text.y = element_text(hjust = 0.5)) + geom_label(vjust=-0.5,hjust=0.25,fill="white") + labs(caption="Note marginal effects for respondent race & partisanship relative to baseline factor categories. Contextual regions omitted. \nFactor Baselines: white respondents, Republican identifiers. * p < 0.1; ** p < 0.05; *** p < 0.01") + facet_wrap(~model) 
ggsave(file="latent_scientific_trust_model_full.png", plot, width = 8, height = 5.43, units = "in")
```