---
title: "Extension_FINAL"
author: "Solome Haile"
date: "2023-04-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readstata13)
library(ggplot2)
library(reshape2)
library(plyr)
library(margins)
library(descr)
library(sandwich)
library(pscl)
library(psych)
library(effects)
library(multiwayvcov)
library(mirt)
library(moments)
library(haven)
library(datawizard)
library(tidyverse)
library(labelled)
#setting working directory (Beza-- be sure to comments this out and set your own when you are coding!)
knitr::opts_knit$set(root.dir = "/Users/solomonaberash/Desktop/Graduate School/SP23 STATS/Rep Paper/BS-rep")

#Beza's working directory 
#knitr::opts_knit$set(root.dir = "/Users/bezataddess/Dropbox (Princeton)/Beza$SolomeReplication/Replication.stats")

```

# Data Wrangling

```{r}
# Load Pew Data
pew <- read.dta13("ATP_W64.dta")
pew <- subset(pew,select=c(QKEY,COVID_COMFORT_a_W64,
                           COVID_COMFORT_b_W64,COVID_COMFORT_c_W64,
                           COVID_COMFORT_d_W64,COVID_COMFORT_e_W64,
                           COVID_RESTRICTION_a_W64,COVID_RESTRICTION_b_W64,
                           COVID_RESTRICTION_c_W64,COVID_RESTRICTION_d_W64,
                           COVID_RESTRICTION_e_W64,COVID_RESTRICTION_f_W64,
                           COVID_RESTRICTION_g_W64,F_IDEO,F_PARTY_FINAL,F_SEX,
                           F_AGECAT,F_EDUCCAT2,F_MARITAL,F_INCOME,F_CREGION,
                           F_RACETHN,WEIGHT_W64))

```

## Code & Scale Ideological DV of interest (policy support)
```{r, warning=FALSE}
covid_ideo_scales <- subset(pew,select=c(QKEY,COVID_RESTRICTION_a_W64,
                                         COVID_RESTRICTION_b_W64,
                                         COVID_RESTRICTION_c_W64,
                                         COVID_RESTRICTION_d_W64,
                                         COVID_RESTRICTION_e_W64,
                                         COVID_RESTRICTION_f_W64,
                                         COVID_RESTRICTION_g_W64,F_IDEO))
colnames(covid_ideo_scales) <- c("QKEY","restriction_intl_travel",
                                 "restriction_most_business",
                                 "restriction_large_gatherings",
                                 "restriction_sporting_events",
                                 "restriction_closing_k12",
                                 "restriction_carry_out_only",
                                 "restriction_postponing_primary","libcon")

for(i in 2:ncol(covid_ideo_scales)){
  covid_ideo_scales[,i] <- as.character(covid_ideo_scales[,i])
}
covid_ideo_scales[covid_ideo_scales == "Necessary"] <- 1
covid_ideo_scales[covid_ideo_scales == "Unnecessary"] <- 0

covid_ideo_scales$libcon <- ifelse(covid_ideo_scales$libcon %in% "Very conservative",1,
                            ifelse(covid_ideo_scales$libcon %in% "Conservative",2,
                            ifelse(covid_ideo_scales$libcon %in% "Moderate",3,
                            ifelse(covid_ideo_scales$libcon %in% "Liberal",4,
                            ifelse(covid_ideo_scales$libcon %in% "Liberal",4,
                            ifelse(covid_ideo_scales$libcon %in% "Very liberal",5,NA))))))


for(i in 2:ncol(covid_ideo_scales)){
  covid_ideo_scales[,i] <- as.numeric(covid_ideo_scales[,i])
}
covid_ideo_scales <- na.omit(covid_ideo_scales)
```

## Factor Analysis (policy support)

```{r, warning=FALSE}
library("FactoMineR")
library("factoextra")

x <- covid_ideo_scales[,c(2:9)]
for(i in 1:8){
  x[,i] <- factor(x[,i])
}

factanal <- FAMD(x, graph = F,ncp=7,sup.var = NULL)
# fviz_screeplot(factanal)
# fviz_contrib(factanal, "var", axes = 1)
# fviz_contrib(factanal, "var", axes = 2)
# fviz_contrib(factanal, "var", axes = 3)
# fviz_famd_var(factanal, "var", repel = TRUE, col.var = "black")

factanal <- fa(covid_ideo_scales[,c(2:9)], nfactors=2, rotate="promax", fm="pa")
scores <- data.frame(factanal$scores)
#loadings(factanal)
loadings <- factanal$loadings
loadings <- data.frame(f1 = loadings[,1],f2=loadings[,2])

#plot(factanal$loadings,type="n") # set up plot 
#text(factanal$loadings,labels=names(covid_ideo_scales)[2:9],cex=.7) # add variable names

library(ggrepel)

#alpha(covid_ideo_scales[,c(2:9)])

library(grid)
library(gridExtra)
loadings$vars <- ifelse(rownames(loadings) %in% "restriction_intl_travel",
                        "International Travel",
                ifelse(rownames(loadings) %in% "restriction_most_business",
                               "Most Businesses",
                ifelse(rownames(loadings) %in% "restriction_large_gatherings",
                                      "Large Gatherings",
                ifelse(rownames(loadings) %in% "restriction_sporting_events",
                                             "Sporting Events",
                ifelse(rownames(loadings) %in% "restriction_closing_k12",
                                                    "K-12 Schools",
                ifelse(rownames(loadings) %in% "restriction_carry_out_only",
                                                           "Carry-out Only",
                ifelse(rownames(loadings) %in% "restriction_postponing_primary",
                                                                  "Postponing Primary",
                ifelse(rownames(loadings) %in% "libcon","Left-Right Ideology",NA))))))))

plot <- ggplot(loadings,aes(x = f1, y=f2,label=vars)) + 
  theme_minimal() + geom_label_repel() + 
  scale_x_continuous("First Dimension Factor (Proportion of Variance: 36%)") + 
  scale_y_continuous("Second Dimension Factor (Propoportion of Variance 4%)") + 
  geom_segment(aes(x = 0,y = 0,xend = f1,yend = f2),arrow=arrow()) 
grid.newpage()

footnote <- expression("Cronbach's Standardized"~alpha~"="~0.78)

g <- arrangeGrob(plot, bottom = textGrob(footnote, x = 0.025, hjust = 0, 
                                         vjust= 0, y=0.75, 
                                         gp = gpar(fontface = "italic", 
                                                   fontsize = 9, col = "black")))
grid.draw(g)
ggsave(file="factor_analysis_covid19_policies.png", g, width = 8, height = 5.43, units = "in")

covid_ideo_scales <- cbind(covid_ideo_scales,scores)
colnames(covid_ideo_scales)[10:11] <- c("covid_restriction_fa_dim1","covid_restriction_fa_dim2")
covid_ideo_scales$summated_restriction_scale <- rowSums(covid_ideo_scales[2:8],na.rm=T)
```


# IRT

```{r}
irt <- mirt(covid_ideo_scales[2:8], model = 1, itemtype = "graded", SE = T, 
            verbose = T,removeEmptyRows = TRUE)
plt <- plot(irt, type = 'trace', facet_items=F) #store the object
print(plt) #plot the object
#str(plt) #find the data
pltdata <- data.frame(lapply(plt$panel.args, function(x) do.call(cbind, x))[[1]])

groups <- plot(irt, type = 'trace', facet_items=T)
groups$packet.sizes
pltdata$item <- rep(colnames(covid_ideo_scales)[2:8], each = 200)
pltdata$response <- groups$panel.args.common$groups

#plt$panel.args.common$groups

pltdata$item2 <- factor(pltdata$item,levels=c("restriction_carry_out_only",
                                              "restriction_closing_k12",
                                              "restriction_intl_travel",
                                              "restriction_large_gatherings",
                                              "restriction_most_business",
                                              "restriction_postponing_primary",
                                              "restriction_sporting_events"),
                        labels=c("Carry Out Only","Close K-12 Schools","
                                 Restrict Intl. Travel","Restrict Large Gatherings",
                                 "Restrict Most Businesses","Postpone Primary Elections",
                                 "Restrict Sporting Events"))

pltdata$item2 <- factor(pltdata$item2,levels=c("Restrict Intl. Travel",
                                               "Restrict Sporting Events",
                                               "Close K-12 Schools",
                                               "Restrict Large Gatherings",
                                               "Carry Out Only","Restrict Most Businesses",
                                               "Postpone Primary Elections"))

plot <- ggplot(pltdata, aes(x, y,linetype=item2,color=item2)) + 
  geom_line() + scale_x_continuous(expression(theta)) + 
  scale_y_continuous("Pr (Support)") + geom_hline(aes(yintercept = 0.5))  + 
  theme_minimal() + labs(color="Policy",linetype="Policy") + 
  theme(legend.position="bottom") 
#+ scale_colour_grey(start = 0, end = .5) + ggtitle("Ordinal IRT Model Characteric Curves for Emphatic Racism Scale")

#ggsave(file="covid19_restrictions_irt_curves_probs.png", plot, width = 8, height = 5.43, units = "in")
```

## Scores
```{r}
covid_ideo_scales$covid_restriction_fa_dim2 <- fscores(irt, full.scores = TRUE, 
                                                       full.scores.SE = F)
colnames(covid_ideo_scales)[11] <- "covid_restriction_irt"

pew <- merge(pew,covid_ideo_scales,by=c("QKEY"),all=T)
pew$covid_restriction_fa_dim1 <- pew$covid_restriction_fa_dim1-mean(pew$covid_restriction_fa_dim1,na.rm=T)
```

## Covariates
```{r}
pew$female <- as.character(pew$F_SEX)
pew$female <- factor(pew$female,levels=c("Male","Female"))

ggplot(na.omit(pew),aes(x=female,y=covid_restriction_fa_dim1)) + geom_boxplot()

pew$pid3 <- as.character(pew$F_PARTY_FINAL)
pew$pid3 <- factor(pew$pid3,levels=c("Republican","Independent","Democrat"))

pew$weight <- as.numeric(pew$WEIGHT_W64)

pew$age_linear <- as.numeric(factor(pew$F_AGECAT))
pew$age_linear[pew$age_linear %in% 5] <- NA # Get rid of refused

pew$educ_linear <- as.numeric(factor(pew$F_EDUCCAT2))
pew$educ_linear[pew$educ_linear %in% 7] <- NA # Get rid of refused

pew$marital_status <- ifelse(pew$F_MARITAL %in% "Married",1,0)
pew$marital_status[pew$F_MARITAL %in% "Refused"] <- NA # Get rid of refused

pew$income_linear <- as.numeric(factor(pew$F_INCOME))
pew$income_linear[pew$income_linear %in% 10] <- NA # Get rid of refused

pew$region_factor <- pew$F_CREGION
pew$white_respondent <- ifelse(pew$F_RACETHN %in% "White non-Hispanic",1,0)
pew$white_respondent[pew$F_RACETHN %in% "Refused"] <- NA # Get rid of refused

hold <- read.dta13("ATP_W42.dta")
hold <- hold[,c("QKEY", "F_RACECMB")]

pew <- merge(pew,hold,by=c("QKEY"),all=T)

pew$race3 <- ifelse(pew$F_RACETHN %in% "White non-Hispanic","white",
                    ifelse(pew$F_RACETHN %in% "Black non-Hispanic","black",
                           ifelse(pew$F_RACETHN %in% "Hispanic","hispanic",NA)))
pew$race3 <- ifelse(is.na(pew$race3) & pew$F_RACECMB %in% "Asian or Asian-American",
                    "asian",pew$race3)

pew$race3 <- factor(pew$race3,levels=c("white","black","hispanic","asian"))
```

# ADDING RELIGION EXTENSION

```{r}
# load the foreign package to read wa
library(foreign)
# read in the .sav file using read.spss()
dataw46 <- read.spss("ATP W46.sav", to.data.frame = TRUE)
# view the first few rows of your data
#head(dataw46)

```

```{r}
#Subsetting the variables we need for religion 
#colnames(dataw46)
dataw46_subset <- subset(dataw46,
                      select=c(QKEY,CHURCHUNITE_W46,RELIGTRUST_W46,F_RACETHN,
                               F_RACECMB, CONFCLERGY1a_W46,CONFCLERGY1b_W46,
                               CONFCLERGY1c_W46,CONFCLERGY2a_W46,CONFCLERGY2b_W46,
                               CONFCLERGY2e_W46,CONFCLERGY2f_W46,
                            RELIG_INFL2_W46,ETERNAL_W46,CLERGY_RELIG_W46,
                            RELIG_FRIENDLYa_W46,RELIG_FRIENDLYb_W46,
                            RELIG_FRIENDLYc_W46,RELIG_FRIENDLYd_W46,
                            RELIG_FRIENDLYe_W46,RELIG_FRIENDLYf_W46,
                            FRIENDS_W46,F_METRO,F_CREGION,F_SEX,F_AGECAT,
                            F_EDUCCAT2,F_MARITAL,F_INCOME,F_CREGION,F_HISP,
                            F_RACECMB,F_NATIVITY,F_CITIZEN,F_RELIG,
                            F_PARTY_FINAL,F_PARTYSUM_FINAL,F_BORN,
                            F_ATTEND,F_IDEO,F_INCOME,F_INCOME_RECODE, 
                            F_E3,WEIGHT_W46))
#head(dataw46_subset)
#str(dataw46_subset)

# remove rows with missing values
dataw46_subset_complete <- na.omit(dataw46_subset)

# view the first few rows of the cleaned data frame (this might be a problem
#because the number of obs. went from 6364 to 2597; we might have to impute)
#imputing  for missing data: Amelia 

#head(dataw46_subset_complete)

```
#Data Wrangling: Religiousness Measure 

```{r}
##Religiousness as religious affiliation (combine 11 and 12)
#levels(dataw46_subset$F_RELIG)

dataw46_subset <- dataw46_subset %>%
  mutate(affiliation = case_when(
    F_RELIG == "Protestant (for example, Baptist, Methodist, 
    Non-denominational, Lutheran, Presbyterian, Pentecostal,
    Episcopalian, Refo" ~ 1,
    F_RELIG == "Roman Catholic" ~ 2,
    F_RELIG == "Mormon (Church of Jesus Christ of
    Latter-day Saints or LDS)" ~ 3,
    F_RELIG == "Orthodox (such as Greek, Russian, 
    or some other Orthodox church)" ~ 4,
    F_RELIG == "Jewish" ~ 5,
    F_RELIG == "Muslim" ~ 6,
    F_RELIG == "Buddhist" ~ 7,
    F_RELIG == "Hindu" ~ 8,
    F_RELIG == "Atheist" ~ 9,
    F_RELIG == "Agnostic" ~ 10,
    F_RELIG == "Something else, Specify" ~ 11,
    F_RELIG == "Nothing in particular" ~ 12,
    F_RELIG == "Refused" ~ 13,
    TRUE ~ NA_integer_
  )) 
  
##Religiousness as religious attendance (seldom and a few times a year) 1 and 2: 
##often, 3: sometime 4 and 5: rarely and never : 6 and refused (as missing)
#levels(dataw46_subset$F_ATTEND)

dataw46_subset <- dataw46_subset %>%
  mutate(attendance = case_when(
    F_ATTEND %in% c("More than once a week", "Once a week") ~ "often",
    F_ATTEND %in% c("Once or twice a month", "A few times a year",
                    "Seldom") ~ "sometimes",
    F_ATTEND %in% c("Never", "Refused") ~ "never",
    TRUE ~ F_ATTEND
  )) %>%
  mutate(attendance = factor(attendance, levels = c("never", 
                                                    "rarely", 
                                                    "sometimes", 
                                                    "often")))
dataw46_subset$attendance <- as.numeric(factor(dataw46_subset$attendance, 
                                               levels = c("never", "rarely", 
                                                          "sometimes",
                                                          "often")))


##Religiousness as religious as belief as relational  
#levels(dataw46_subset$ETERNAL_W46)
dataw46_subset$eternal_life <- ifelse(dataw46_subset$ETERNAL_W46 == "My religion
                                      is the one true faith leading 
                                      to eternal life", 1,
                                      ifelse(dataw46_subset$ETERNAL_W46 == "Many
                                             religions can lead to eternal
                                             life", 2,
                                   ifelse(is.na(dataw46_subset$ETERNAL_W46) | 
                          dataw46_subset$ETERNAL_W46 == "Refused", NA, NA)))

##Religiousness as religious as  belief as shaping your way of life 
##(interpersonal life and world)
# levels(dataw46_subset$CONFCLERGY1a_W46)
# levels(dataw46_subset$CONFCLERGY1b_W46)
# levels(dataw46_subset$CONFCLERGY1c_W46)
# levels(dataw46_subset$CONFCLERGY2a_W46)
# levels(dataw46_subset$CONFCLERGY2b_W46)
# levels(dataw46_subset$CONFCLERGY2e_W46)
# levels(dataw46_subset$CONFCLERGY2f_W46)


dataw46_subset <- dataw46 %>%
  mutate(CONFCLERGY1a_W46 = recode(CONFCLERGY1a_W46, 
                                   "A lot of confidence" = 4,
                                   "Some confidence" = 3,
                                   "Not much confidence" = 2,
                                   "No confidence at all" = 1),
         
         CONFCLERGY1b_W46 = recode(CONFCLERGY1b_W46, 
                                   "A lot of confidence" = 4,
                                   "Some confidence" = 3,
                                   "Not much confidence" = 2,
                                   "No confidence at all" = 1),
         
         CONFCLERGY1c_W46 = recode(CONFCLERGY1c_W46, 
                                   "A lot of confidence" = 4,
                                   "Some confidence" = 3,
                                   "Not much confidence" = 2,
                                   "No confidence at all" = 1),
         
         CONFCLERGY2a_W46 = recode(CONFCLERGY2a_W46, 
                                   "A lot of confidence" = 4,
                                   "Some confidence" = 3,
                                   "Not much confidence" = 2,
                                   "No confidence at all" = 1),
         
         CONFCLERGY2b_W46 = recode(CONFCLERGY2b_W46, 
                                   "A lot of confidence" = 4,
                                   "Some confidence" = 3,
                                   "Not much confidence" = 2,
                                   "No confidence at all" = 1),
         
         CONFCLERGY2e_W46 = recode(CONFCLERGY2e_W46, 
                                   "A lot of confidence" = 4,
                                   "Some confidence" = 3,
                                   "Not much confidence" = 2,
                                   "No confidence at all" = 1),
         
         CONFCLERGY2f_W46 = recode(CONFCLERGY2f_W46, 
                                   "A lot of confidence" = 4,
                                   "Some confidence" = 3,
                                   "Not much confidence" = 2,
                                   "No confidence at all" = 1
                                  ))


```

# Trust variable w/ religion

```{r}
trust <- read.dta13("ATP_W42.dta")
trust <- subset(trust,select=c("QKEY","CONFa_W42","CONFb_W42", "CONFe_W42","CONFd_F1_W42","CONFd_F2_W42",  "POLICY1_W42","POLICY2_W42","POLICY3_W42","SCM2_W42","SCM3_W42","SCM4a_W42","SCM4b_W42"))

colnames(trust) <- c("QKEY","trust_elected_officials","trust_media","trust_religious","trust_medial_scientists","trust_scientists","scientists_active_role_policy","scientists_pivotal_policy","scientists_better_policy","scientific_method","scientists_judgement_facts","research_essential_immediate_applications","research_essential_advance_knowledge")

trust[trust == "Refused"] <- NA

for(i in 2:ncol(trust)){
  print(table(trust[,i]))
  print(levels(trust[,i]))
}
for(i in 2:ncol(trust)){
  trust[,i] <- as.character(trust[,i])
  print(table(trust[,i]))
}  
trust[trust == "Essential"] <- 4
trust[trust == "Important, but not essential"] <- 3
trust[trust == "Not too important"] <- 2
trust[trust == "Not important at all"] <- 1

trust[trust == "A great deal of confidence"] <- 4
trust[trust == "A fair amount of confidence"] <- 3
trust[trust == "Not too much confidence"] <- 2
trust[trust == "No confidence at all"] <- 1

trust[trust == "Scientists should take an active role in public policy debates about scientific issues"] <- 2
trust[trust == "Scientists should focus on establishing sound scientific facts and stay out of public policy debates"] <- 1

trust[trust == "Public opinion should NOT play an important role to guide policy decisions about scientific issues because these issues"] <- 2
trust[trust == "Public opinion should play an important role to guide policy decisions about scientific issues"] <- 1

trust[trust == "Usually BETTER at making good policy decisions about scientific issues than other people"] <- 3
trust[trust == "NEITHER BETTER NOR WORSE at making good policy decisions about scientific issues than other people"] <- 2
trust[trust == "Usually WORSE at making good policy decisions about scientific issues than other people"] <- 1

trust[trust == "The scientific method generally produces accurate conclusions"] <- 2
trust[trust == "The scientific method can be used to produce any conclusion the researcher wants"] <- 1

trust[trust == "Scientists make judgments based solely on the facts"] <- 2
trust[trust == "Scientists' judgments are just as likely to be biased as other people's"] <- 1

trust$trust_scientists <- ifelse(is.na(trust$trust_medial_scientists),trust$trust_scientists,ifelse(is.na(trust$trust_scientists),trust$trust_medial_scientists,NA))

trust$trust_medial_scientists <- NULL
trust$scientists_pivotal_policy <- NULL

for(i in 2:ncol(trust)){
  trust[,i] <- as.numeric(trust[,i])
  print(table(trust[,i]))
}  

factanal <- fa(trust[,c(5:11)], nfactors=2, rotate="promax", fm="pa")
scores <- data.frame(factanal$scores)
loadings(factanal)
loadings <- factanal$loadings
loadings <- data.frame(f1 = loadings[,1],f2=loadings[,2])

# plot(factanal$loadings,type="n") # set up plot 
# text(factanal$loadings,labels=names(trust)[4:10],cex=.7) # add variable names

library(ggrepel)

# alpha(trust[,c(4:8)])
# skewness(loadings$f1, na.rm=T)
# kurtosis(loadings$f1, na.rm=T)
# 
# alpha(trust[,c(9:10)])
# skewness(loadings$f2, na.rm=T)
# kurtosis(loadings$f2, na.rm=T)

loadings$vars <- ifelse(rownames(loadings) %in% "trust_scientists",
                        "Trust Scientists",
                  ifelse(rownames(loadings) %in% "scientists_active_role_policy",
                         "Scientists Active Role Policy",
                  ifelse(rownames(loadings) %in% "scientists_pivotal_policy",
                         "PO Guiding Policy Science",
                  ifelse(rownames(loadings) %in% "scientists_better_policy",
                         "Scientists Better Policymakers",
                  ifelse(rownames(loadings) %in% "scientific_method",
                         "Scientific Method Validity",
                  ifelse(rownames(loadings) %in% "scientists_judgement_facts",
                         "Unbiased Scientists",
                  ifelse(rownames(loadings) %in% "research_essential_immediate_applications",
                         "Research Essential Applications",
                  ifelse(rownames(loadings) %in% "research_essential_advance_knowledge",
                         "Research Essential Knowledge",NA))))))))

plot <- ggplot(loadings,aes(x = f1, y=f2,label=vars)) + theme_minimal() + geom_label_repel() + scale_x_continuous("First Dimension Factor") + scale_y_continuous("Second Dimension Factor") + geom_segment(aes(x = 0,y = 0,xend = f1,yend = f2),arrow=arrow())  # (Proportion of Variance F1: 18%) (Proportion of F2 Variance 16%)"

grid.newpage()
footnote <- expression("Cronbach's Standardized"~alpha~"="~0.66)
g <- arrangeGrob(plot, bottom = textGrob(footnote, x = 0.025, hjust = 0, vjust= 0, y=0.75, gp = gpar(fontface = "italic", fontsize = 9, col = "black")))
grid.draw(g)

#ggsave(file="factor_analysis_scientific_trust.png", g, width = 8, height = 5.43, units = "in")

trust <- cbind(trust,scores)
colnames(trust)[12:13] <- c("trust_scientists_fa_dim1","trust_scientists_fa_dim2")

## Merging Data Sets
pew <- merge(pew,trust,by=c("QKEY"),all=T)

x <- subset(pew,select=c(pid3,trust_scientists_fa_dim1,trust_scientists_fa_dim2))
x <- na.omit(x)
x$pid <- ifelse(x$pid3 %in% "Democrat","D",
                ifelse(x$pid3 %in% "Republican","R",
                       ifelse(x$pid3 %in% "Independent","I",NA)))

plot <- ggplot(x,aes(x=trust_scientists_fa_dim1,
                     y=trust_scientists_fa_dim2,label=pid,color=pid)) + 
  geom_text(alpha=0.2) + scale_color_manual("",values=c("blue","purple","red"))

x1 <- x
x1$pid3 <- "Full Sample"
x <- rbind(x,x1)
x$pid3 <- factor(x$pid3,levels=c("Republican","Independent","Democrat","Full Sample"),
                 labels=c("Republican Partisans","Independent Partisans",
                          "Democratic Partisans","Full Sample"))

print(summary(aov(trust_scientists_fa_dim1 ~ pid3, data = x)))

plot <- ggplot(x, aes(x=pid3,y=trust_scientists_fa_dim1, group=pid3,fill=pid3)) + 
  geom_boxplot(alpha=0.2) + theme_minimal() +
  scale_y_continuous("Latent Scientific Trust") + 
  scale_x_discrete("") + scale_fill_manual("",values=c("red","purple","blue","black")) + 
  theme(legend.position = "none") 
#ggsave(file="scientific_trust_boxplots_by_party.png", plot, width = 8, height = 5.43, units = "in")

```
# Adding Trust in Religious Leaders

# Data Analysis: COVID Policy ~ Scientific Trust: Baseline Effects

## Baseline Trust Effects
```{r, warning=FALSE}
baseline_trust_effects <- list()
for(i in which(colnames(pew) == "restriction_intl_travel"):
    which(colnames(pew) == "restriction_postponing_primary")){
  summary(model <- glm(pew[,i] ~ trust_scientists_fa_dim1 + 
                         trust_media + trust_elected_officials + trust_religious + 
                         female + pid3 + libcon + age_linear + educ_linear + 
                         income_linear + race3 + region_factor, 
                       data=pew, weights=weight, family = binomial(link = "logit")))
  mes <- summary(margins(model, 
                         variables=c("trust_scientists_fa_dim1","trust_media", 
                                     "trust_religious",
                                     "trust_elected_officials"),
                         type="response", change="minmax"))
  mes$model <- colnames(pew)[i]
  mes$category <- "Full Sample Baseline"
  baseline_trust_effects[[i]] <- mes
}
baseline_trust_effects <- ldply(baseline_trust_effects,data.frame)

baseline_trust_effects$pid3 <- "Full Baseline Sample"
baseline_trust_effects$category <- NULL

effects <- baseline_trust_effects
effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))
effects$model2 <- ifelse(effects$model %in% "restriction_carry_out_only",
                         "Dependent Variable: Restaurants Carry Out Only",
                  ifelse(effects$model %in% "restriction_closing_k12",
                         "Dependent Variable: Close K-12 Schools",
                  ifelse(effects$model %in% "restriction_intl_travel",
                         "Dependent Variable: Restrict International Travel",
                  ifelse(effects$model %in% "restriction_large_gatherings",
                         "Dependent Variable: Restrict Large Gatherings",
                  ifelse(effects$model %in% "restriction_most_business",
                         "Dependent Variable: Restrict Most Businesses",
                  ifelse(effects$model %in% "restriction_postponing_primary",
                         "Dependent Variable: Postpone Primary Elections",
                  ifelse(effects$model %in% "restriction_sporting_events",
                         "Dependent Variable: Restrict Sporting Events",NA)))))))

effects$factor <- ifelse(effects$factor %in% "trust_elected_officials","Elected Officials Trust",
                  ifelse(effects$factor %in% "trust_media","Media Trust",
                  ifelse(effects$factor %in% "trust_religious","Religious Leader Trust",
                  ifelse(effects$factor %in% "trust_scientists_fa_dim1","Scientific Trust",NA))))

effects$label <- ifelse(effects$p < 0.01,paste(round(effects$AME,2),"***",sep=""),
                  ifelse(effects$p < 0.05,paste(round(effects$AME,2),"**",sep=""),
                  ifelse(effects$p < 0.10,paste(round(effects$AME,2),"*",sep=""),NA)))

for(i in unique(effects$model)){
  x <- subset(effects,effects$model %in% i)
  plot <- ggplot(x,aes(x=factor,y=AME,factor=factor,group=factor,color=factor,
                       shape=factor,label=label,fill=factor)) + 
    facet_wrap(~model2) + coord_flip() + 
    geom_linerange(aes(x= factor, ymin = ylo90, ymax = yhi90), 
                   position = position_dodge(width=0.75), lwd  = 1) + 
    geom_pointrange(aes(x= factor, ymin = lower, ymax = upper), lwd = 1/2, 
                    position = position_dodge(width=0.75),fill="white") + 
    theme_minimal() + scale_x_discrete("") + 
    scale_y_continuous("Min/Max First Difference Marginal Effects on 
                       Pr(Necessary Government Policy)") + 
    geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  
    labs(color="Trust Effects",shape="Trust Effects") + 
    theme(legend.position = "none") + 
    theme(axis.text.x = element_text(hjust = 0.5),
          axis.text.y = element_text(hjust = 0.5)) + 
    geom_label(vjust=-0.5,hjust=0.25,fill="white") + 
    labs(caption="* p < 0.1; ** p < 0.05; *** p < 0.01") + 
    scale_shape_manual("",values=c(23,22,21,20))
  print(plot)
  #ggsave(file=paste(i,"_model",".png",sep=""), plot, width = 8, height = 5.43, units = "in")
}
```



# Data Analysis Figures: OLS Composite Models
```{r, warning=FALSE, eval=FALSE}
model <- glm(covid_restriction_irt ~ trust_scientists_fa_dim1 + 
                       trust_media + + trust_religious + trust_elected_officials + 
                       female + libcon + age_linear + educ_linear + 
                       income_linear + race3 + region_factor, 
                     data=pew, weights=weight, family = gaussian(identity))

baseline_trust_effects.2 <- summary(margins(model, 
                                  variables=c("trust_scientists_fa_dim1","trust_media", 
                                     "trust_religious",
                                     "trust_elected_officials"), 
                                            type="response", change="minmax"))
baseline_trust_effects.2$model <- "DV: Latent Policy Scale"
baseline_trust_effects.2$pid3 <- "Full Sample"

effects <- baseline_trust_effects.2
effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))
effects$ame_label <- round(effects$AME,2)
effects$factor <- ifelse(effects$factor %in% "trust_elected_officials","Elected Officials Trust",
                  ifelse(effects$factor %in% "trust_media","Media Trust",
                  ifelse(effects$factor %in% "trust_religious","Religious Leader Trust",
                  ifelse(effects$factor %in% "trust_scientists_fa_dim1","Scientific Trust",NA))))
effects$label <- ifelse(effects$p < 0.01,paste(round(effects$AME,2),"***",sep=""),
                  ifelse(effects$p < 0.05,paste(round(effects$AME,2),"**",sep=""),
                  ifelse(effects$p < 0.10,paste(round(effects$AME,2),"*",sep=""),NA)))

plot <- ggplot(effects,aes(x=factor,y=AME,factor=factor,
                           group=factor,color=factor,shape=factor,label=label,fill=factor)) + 
  facet_wrap(~model) + coord_flip() + 
  geom_linerange(aes(x= factor, ymin = ylo90, ymax = yhi90), 
                 position = position_dodge(width=0.75), lwd  = 1) + 
  geom_pointrange(aes(x= factor, ymin = lower, ymax = upper), lwd = 1/2, 
                  position = position_dodge(width=0.75),fill="white") + 
  theme_minimal() + scale_x_discrete("") + 
  scale_y_continuous("Min/Max First Difference Marginal Effects on 
                     Latent Necessary Government Policies")  + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  
  labs(color="Trust Effects",shape="Trust Effects") + 
  theme(legend.position = "none") + 
  theme(axis.text.x = element_text(hjust = 0.5),axis.text.y = element_text(hjust = 0.5)) + 
  geom_label(vjust=-0.5,hjust=0.25,fill="white") + 
  labs(caption="* p < 0.1; ** p < 0.05; *** p < 0.01") + 
  scale_shape_manual("",values=c(23,22,21))
#ggsave(file="latent_policy_scale_model.png", plot, width = 8, height = 5.43, units = "in")

model <- glm(summated_restriction_scale ~ trust_scientists_fa_dim1 + 
                       trust_media + trust_elected_officials + trust_religious + female + 
                       libcon + age_linear + educ_linear + income_linear + 
                       race3 + region_factor, data=pew, weights=weight, 
                     family = "poisson")
baseline_trust_effects.3 <- summary(margins(model, 
                                            variables=c("trust_scientists_fa_dim1",
                                                        "trust_media","trust_elected_officials"),
                                            type="response", change="minmax"))
baseline_trust_effects.3$model <- "DV: Summated Policy Scale"
baseline_trust_effects.3$pid3 <- "Full Sample"

effects <- baseline_trust_effects.3
effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))
effects$ame_label <- round(effects$AME,2)
effects$factor <- ifelse(effects$factor %in% "trust_elected_officials","Elected Officials Trust",
                  ifelse(effects$factor %in% "trust_media","Media Trust",
                  ifelse(effects$factor %in% "trust_religious","Religious Leader Trust",
                  ifelse(effects$factor %in% "trust_scientists_fa_dim1","Scientific Trust",NA))))
effects$label <- ifelse(effects$p < 0.01,paste(round(effects$AME,2),"***",sep=""),
                ifelse(effects$p < 0.05,paste(round(effects$AME,2),"**",sep=""),
                  ifelse(effects$p < 0.10,paste(round(effects$AME,2),"*",sep=""),NA)))

plot <- ggplot(effects,aes(x=factor,y=AME,
                           factor=factor,group=factor,
                           color=factor,shape=factor,label=label)) + 
  facet_wrap(~model) + coord_flip() +
  geom_linerange(aes(x= factor, ymin = ylo90, ymax = yhi90), 
                 position = position_dodge(width=0.75), lwd  = 1) + 
  geom_pointrange(aes(x= factor, ymin = lower, ymax = upper), lwd = 1/2, 
                  position = position_dodge(width=0.75),fill="white") + 
  theme_minimal() + scale_x_discrete("") + 
  scale_y_continuous("Min/Max First Difference Marginal Effects on 
                     Number of Necessary Government Policies")  + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  
  labs(color="Trust Effects",shape="Trust Effects") + theme(legend.position = "none") +
  theme(axis.text.x = element_text(hjust = 0.5),
        axis.text.y = element_text(hjust = 0.5)) + 
  geom_label(vjust=-0.5,hjust=0.25,fill="white") + 
  labs(caption="* p < 0.1; ** p < 0.05; *** p < 0.01") + 
  scale_shape_manual("",values=c(23,22,21))
print(plot)
#ggsave(file="summated_policy_scale_model.png", plot, width = 8, height = 5.43, units = "in")
```

# Distribution of Summated Rating Scales
```{r, warning=FALSE, eval= F}
x <- subset(pew,select=c(summated_restriction_scale,trust_scientists_fa_dim1,
                         pid3,trust_media,trust_elected_officials,female,libcon,
                         age_linear,educ_linear,income_linear,white_respondent,
                         region_factor,race3))
x1 <- na.omit(x)
x <- na.omit(x)
x1$race3 <- "Full Sample"

x <- subset(x,select=c(summated_restriction_scale,race3))
x$n <- 1
xs <- ddply(x,.(summated_restriction_scale,race3),summarise,total=sum(n,na.rm=T))
x <- ddply(x,.(race3),summarise,total_race3=sum(n,na.rm=T))
xs <- merge(xs,x,by=c("race3"))
xs$prop <- xs$total/xs$total_race3

x1 <- subset(x1,select=c(summated_restriction_scale,race3))
x1$n <- 1
xs1 <- ddply(x1,.(summated_restriction_scale),summarise,total=sum(n,na.rm=T))
xs1$total_race3 <- sum(x1$n,na.rm=T)
xs1$prop <- xs1$total/xs1$total_race3
xs1$race3 <- "Full Sample"

x <- rbind(xs,xs1)
x$race3 <- factor(x$race3,
                  levels=c("asian","black","hispanic","white","Full Sample"),
                  labels=c("Asian Respondents","Black Respondents",
                           "Hispanic Respondents","White Respondents","Full Sample"))

plot <- ggplot(x, aes(x=factor(summated_restriction_scale), 
                      y=prop, label=round(prop,2))) + 
  geom_point(stat='identity', size=6*1.25) + 
  geom_segment(aes(y=0,x=factor(summated_restriction_scale),
                   yend=prop,xend=factor(summated_restriction_scale)))+ 
  geom_text(color="white", size=2*1.25) + coord_flip() + 
  facet_wrap(~race3) + theme_minimal() + theme(legend.position = "none") + 
  scale_x_discrete("Number of Restrictive COVID-19 Policies Necessary") + 
  scale_y_continuous("Proportion of Respondents")
#ggsave(file="number_policies_dotplot.png", plot, width = 8, height = 5.43, units = "in")
```









#Covariates: 

```{r, eval= FALSE}
library(tidyverse)
#Transforming gender covariate 
dataw46_subset$female <- as.character(dataw46_subset$F_SEX)
dataw46_subset$female <- recode(dataw46_subset$female, "1" = "Male", "2"= "Female")
dataw46_subset$female <- factor(dataw46_subset$female, levels=c("Male","Female"))

#Transforming & cleaning age covariate
dataw46_subset$age_linear <- as.factor(factor(dataw46_subset$F_AGECAT))
dataw46_subset$age_linear[dataw46_subset$age_linear %in% 5] <- NA # Get rid of refused

#transforming & cleaning education covariate
dataw46_subset$educ_linear <- as.factor(factor(dataw46_subset$F_EDUCCAT2))
dataw46_subset$educ_linear[dataw46_subset$educ_linear %in% 7] <- NA # Get rid of refused

#transforming & cleaning marital covariate
dataw46_subset$marital_status <- ifelse(dataw46_subset$F_MARITAL %in% "Married",1,0)
dataw46_subset$marital_status[dataw46_subset$F_MARITAL %in% "Refused"] <- NA # Get rid of refused

#transforming & cleaning income covariate
dataw46_subset$income_linear <- as.factor(factor(dataw46_subset$F_INCOME))
dataw46_subset$income_linear[dataw46_subset$income_linear %in% 10] <- NA # Get rid of refused

#transforming & cleaning region & white race covariates
library(dplyr)

dataw46_subset <- dataw46_subset %>% 
  mutate(region_factor = F_CREGION,
         white_respondent = case_when(F_RACETHN == "White non-Hispanic" ~ 1,
                                      F_RACETHN != "White non-Hispanic" ~ 0,
                                      TRUE ~ NA_real_)
        )

#getting other race covariate and merging with the dataw46_subset data 
library(haven)
dataw42 <- read_dta("ATP_W42.dta")
dataw42_sub <- dataw42[,c("QKEY", "F_RACECMB")]

dim(dataw46_subset)
dim(dataw42)

dataw46_subset <- merge(dataw46_subset, dataw42_sub, 
                        by = "QKEY",
                        all = TRUE, suffixes = c("_w46", "_w42"))

dataw46_subset$dataw42_sub <- ifelse(dataw46_subset$F_RACETHN %in% "White non-Hispanic","white",ifelse(dataw46_subset$F_RACETHN %in% "Black non-Hispanic",
                                                                                                       "black",ifelse(dataw46_subset$F_RACETHN %in% "Hispanic","hispanic",NA)))
dataw46_subset$dataw42_sub <- ifelse(is.na(dataw46_subset$dataw42_sub) & dataw46_subset$F_RACECMB %in% "Asian or Asian-American","asian",dataw46_subset$dataw42_sub)

dataw46_subset$dataw42_sub <- factor(dataw46_subset$dataw42_sub,levels=c("white","black","hispanic","asian"))

```

#Run first pass of analysis 

```{r, eval=FALSE}
#Linear model: religion as affiliation on scientific trust 
relig_trust <- lm(affiliation ~ trust_scientists_fa_dim1 + 
                    marital_status + income_linear + 
                    educ_linear + age_linear + female,
          data = dataw64_subset)

#Linear model: religion as eternal_life on scientific trust 
relig_trust <- lm(eternal_life ~ trust_scientists_fa_dim1 + 
                    marital_status + income_linear + 
                    educ_linear + age_linear + female,
          data = dataw64_subset)

#Linear model: religion as attendance on scientific trust 
relig_trust <- lm(attendance ~ trust_scientists_fa_dim1 + 
                    marital_status + income_linear + 
                    educ_linear + age_linear + female,
          data = dataw64_subset)

#Linear model: religion as CONFCLERGY1a_W46 on scientific trust 
relig_trust <- lm(CONFCLERGY1a_W46 ~ trust_scientists_fa_dim1 + 
                    marital_status + income_linear + 
                    educ_linear + age_linear + female,
          data = dataw64_subset)
```



# Conditioned by Race | Data Analysis: COVID Policy ~ Scientific Trust: Baseline Effects [W/ TRUST IN RELIGIOUS INSTITUTIONS]

## Baseline Trust Effects
```{r, warning=FALSE, eval=FALSE}
baseline_trust_effects.race <- list()
for(i in which(colnames(pew) == "restriction_intl_travel"):
    which(colnames(pew) == "restriction_postponing_primary")){
  summary(model <- glm(pew[,i] ~ trust_scientists_fa_dim1*race3 + 
                         trust_media + trust_elected_officials + 
                         female + pid3 + libcon + age_linear + 
                         educ_linear + income_linear + 
                         region_factor, data=pew, weights=weight, 
                       family = binomial(link = "logit")))
  mes <- summary(margins(model, 
                         variables=c("trust_scientists_fa_dim1","trust_media",
                                     "trust_elected_officials"),
                         at=list(race3=c("asian","black","white","hispanic")), 
                         type="response", change="minmax",))
  mes$model <- colnames(pew)[i]
  mes$category <- "Full Sample Baseline"
  baseline_trust_effects.race[[i]] <- mes
}
baseline_trust_effects.race <- ldply(baseline_trust_effects.race,data.frame)


effects <- baseline_trust_effects.race
effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))
effects$model2 <- ifelse(effects$model %in% "restriction_carry_out_only",
                         "Dependent Variable: Restaurants Carry Out Only",
                  ifelse(effects$model %in% "restriction_closing_k12",
                         "Dependent Variable: Close K-12 Schools",
                  ifelse(effects$model %in% "restriction_intl_travel",
                         "Dependent Variable: Restrict International Travel",
                  ifelse(effects$model %in% "restriction_large_gatherings",
                         "Dependent Variable: Restrict Large Gatherings",
                  ifelse(effects$model %in% "restriction_most_business",
                         "Dependent Variable: Restrict Most Businesses",
                  ifelse(effects$model %in% "restriction_postponing_primary",
                         "Dependent Variable: Postpone Primary Elections",
                  ifelse(effects$model %in% "restriction_sporting_events",
                         "Dependent Variable: Restrict Sporting Events",NA)))))))
effects$factor <- ifelse(effects$factor %in% "trust_elected_officials",
                         "Elected Officials Trust",
                  ifelse(effects$factor %in% "trust_media","Media Trust",
                  ifelse(effects$factor %in% "trust_scientists_fa_dim1",
                         "Scientific Trust",NA)))
effects$race3 <- factor(effects$race3,levels=c("asian","black","white","hispanic"), 
                        labels=c("Asian Respondents","Black Respondents",
                                 "White Respondents","Hispanic Respondents"))

for(i in unique(effects$model)){
  x <- subset(effects,effects$model %in% i)
  plot <- ggplot(x,aes(x=race3,y=AME,factor=factor,group=factor,
                       color=factor,shape=factor)) +
    facet_wrap(~model2) + coord_flip() + 
    geom_linerange(aes(x= race3, ymin = ylo90, ymax = yhi90), 
                   position = position_dodge(width=0.75), lwd  = 1) + 
    geom_pointrange(aes(x= race3, ymin = lower, ymax = upper), lwd = 1/2, 
                    position = position_dodge(width=0.75),fill="white") + 
    theme_minimal() + scale_x_discrete("") + 
    scale_y_continuous("Min/Max First Difference Marginal 
                       Effects on Pr(Necessary Government Policy)") + 
    geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
    labs(color="Trust Effects",shape="Trust Effects") + theme(legend.position = "bottom") + 
    theme(axis.text.x = element_text(hjust = 0.5),axis.text.y = element_text(hjust = 0.5)) + 
    scale_shape_manual("Trust Effects",values=c(23,22,21))
  print(plot)
  #ggsave(file=paste(i,"_race3_model",".png",sep=""), plot, width = 8, height = 5.43, units = "in")
}
```

# Data Analysis Figures: OLS Composite Models
```{r, warning=FALSE, eval=FALSE}
model <- glm(covid_restriction_irt ~ trust_scientists_fa_dim1*race3 + 
                       trust_media*race3 + trust_elected_officials*race3 + 
                       female + libcon + age_linear + educ_linear + 
                       income_linear + region_factor, data=pew, 
                     weights=weight, family = gaussian(identity))
baseline_trust_effects.4 <- summary(margins(model, 
                                            variables=c("trust_scientists_fa_dim1",
                                                        "trust_media","trust_elected_officials"),
                                            at=list(race3=c("asian","white","black","hispanic")), 
                                            type="response", change="minmax"))
baseline_trust_effects.4$model <- "DV: Latent Policy Scale"
baseline_trust_effects.4$pid3 <- "Full Sample"

effects <- baseline_trust_effects.4
effects$race3 <- factor(effects$race3,levels=c("asian","black","white","hispanic"), 
                        labels=c("Asian Respondents","Black Respondents",
                                 "White Respondents","Hispanic Respondents"))

effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))

effects$factor <- ifelse(effects$factor %in% "trust_elected_officials",
                         "Elected Officials Trust",
                  ifelse(effects$factor %in% "trust_media","Media Trust",
                  ifelse(effects$factor %in% "trust_scientists_fa_dim1",
                         "Scientific Trust",NA)))

plot <- ggplot(effects,aes(x=race3,y=AME,factor=factor,group=factor,color=factor,shape=factor)) + 
  facet_wrap(~model) + coord_flip() + 
  geom_linerange(aes(x= race3, ymin = ylo90, ymax = yhi90), 
                 position = position_dodge(width=0.75), lwd  = 1) + 
  geom_pointrange(aes(x= race3, ymin = lower, ymax = upper), lwd = 1/2, 
                  position = position_dodge(width=0.75),fill="white") + 
  theme_minimal() + scale_x_discrete("") + 
  scale_y_continuous("Min/Max First Difference Marginal Effects on 
                     Latent Policy Restriction Scale") + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  
  labs(color="Trust Effects",shape="Trust Effects") + 
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(hjust = 0.5),
        axis.text.y = element_text(hjust = 0.5)) + 
  scale_shape_manual("Trust Effects",values=c(23,22,21))
print(plot)
#ggsave(file="latent_policy_scale_race3_model.png", plot, width = 8, height = 5.43, units = "in")

model <- glm(summated_restriction_scale ~ trust_scientists_fa_dim1*race3 + 
                       trust_media*race3 + trust_elected_officials*race3 + 
                       female + libcon + age_linear + educ_linear + 
                       income_linear + region_factor, data=pew,
                     weights=weight, family = gaussian(identity))
baseline_trust_effects.5 <- summary(margins(model, 
                                            variables=c("trust_scientists_fa_dim1",
                                                        "trust_media",
                                                        "trust_elected_officials"),
                                            at=list(race3=c("asian","white","black",
                                                            "hispanic")), 
                                            type="response", change="minmax"))
baseline_trust_effects.5$model <- "DV: Summated Policy Scale"
baseline_trust_effects.5$pid3 <- "Full Sample"

effects <- baseline_trust_effects.5
effects$race3 <- factor(effects$race3,levels=c("asian","black","white","hispanic"), 
                        labels=c("Asian Respondents","Black Respondents",
                                 "White Respondents","Hispanic Respondents"))

effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))

effects$factor <- ifelse(effects$factor %in% "trust_elected_officials",
                         "Elected Officials Trust",
                  ifelse(effects$factor %in% "trust_media","Media Trust",
                  ifelse(effects$factor %in% "trust_scientists_fa_dim1",
                         "Scientific Trust",NA)))

plot <- ggplot(effects,aes(x=race3,y=AME,factor=factor,group=factor,color=factor,shape=factor)) + 
  facet_wrap(~model) + coord_flip() + 
  geom_linerange(aes(x= race3, ymin = ylo90, ymax = yhi90), 
                 position = position_dodge(width=0.75), lwd  = 1) + 
  geom_pointrange(aes(x= race3, ymin = lower, ymax = upper), lwd = 1/2, 
                  position = position_dodge(width=0.75),fill="white") + 
  theme_minimal() + scale_x_discrete("") + 
  scale_y_continuous("Min/Max First Difference Marginal Effects on 
                     Number of Necessary Government Policies") + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  
  labs(color="Trust Effects",shape="Trust Effects") + 
  theme(legend.position = "bottom") + theme(axis.text.x = element_text(hjust = 0.5),
                                            axis.text.y = element_text(hjust = 0.5)) + 
  scale_shape_manual("Trust Effects",values=c(23,22,21))
print(plot)
#ggsave(file="summated_policy_scale_race3_model.png", plot, width = 8, height = 5.43, units = "in")
```

# Boxplot by Race
```{r, warning=FALSE, eval=FALSE}
x <- subset(pew,select=c(race3,trust_scientists_fa_dim1))
x <- na.omit(x)
print(summary(aov(trust_scientists_fa_dim1 ~ race3, data = x)))
y <- subset(pew,select=c(race3,trust_scientists_fa_dim1))
y$race3 <- "Full Sample"
x <- rbind(x,y)

plot <- ggplot(x, aes(x=race3,y=trust_scientists_fa_dim1, group=race3,fill=race3)) + 
  geom_boxplot(alpha=0.2) + theme_minimal() + 
  scale_y_continuous("Latent Scientific Trust") + 
  scale_x_discrete("",labels=c("White Respondents","Black Respondents",
                               "Hispanic Respondents","Asian Respondents","Full Sample")) + 
  theme(legend.position = "none") + 
  labs(caption="ANOVA suggests significant differences in mean latent 
       scientific trust across racial groups, p < 0.01.") + 
  geom_jitter(aes(colour=race3),alpha=0.075) + 
  scale_color_manual("",values=c("#F8766D","#7CAE00","#00BFC4","#529EFF","gray")) + 
  scale_fill_manual("",values=c("#F8766D","#7CAE00","#00BFC4","#529EFF","gray"))
#ggsave(file="scientific_trust_boxplots_by_race3.png", plot, width = 8, height = 5.43, units = "in")
```

# Data Analysis Figures: OLS Composite Models 
```{r, warning=FALSE, eval=FALSE}
model <- lm(trust_scientists_fa_dim1 ~ female + pid3 + libcon + 
                      age_linear + educ_linear + income_linear + race3 + 
                      region_factor, data=pew, weights=weight)

mes <- summary(margins(model, type="response", change="minmax"))
mes$race3 <- factor(mes$factor,levels=c("race3asian","race3black","race3hispanic"),
                    labels=c("Asian Respondents","Black Respondents",
                             "Hispanic Respondents"))

mes$label <- ifelse(mes$p < 0.01,paste(round(mes$AME,2),"***",sep=""),
                    ifelse(mes$p < 0.05,paste(round(mes$AME,2),"**",sep=""),
                    ifelse(mes$p < 0.10,paste(round(mes$AME,2),"*",sep=""),NA)))

mes$ylo90 <- (mes$AME - (qt(.95, 100) * mes$SE))
mes$yhi90 <- (mes$AME + (qt(.95, 100) * mes$SE))
mes$model <- "DV: Latent Scientific Trust "

plot <- ggplot(subset(mes,!is.na(mes$race3)),
               aes(x=race3,y=AME,factor=race3,group=race3,
                   color=race3,shape=race3,label=label,fill=race3)) + 
  facet_wrap(~model) + coord_flip() + 
  geom_linerange(aes(x= race3, ymin = ylo90, ymax = yhi90), 
                 position = position_dodge(width=0.75), lwd  = 1) + 
  geom_pointrange(aes(x= race3, ymin = lower, ymax = upper), lwd = 1/2, 
                  position = position_dodge(width=0.75),fill="white") + 
  theme_minimal() + scale_x_discrete("") + 
  scale_y_continuous("Marginal Effect of Race on Latent Scientific Trust")  + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  
  labs(color="Trust Effects",shape="Trust Effects") + 
  theme(legend.position = "none") + 
  theme(axis.text.x = element_text(hjust = 0.5),axis.text.y = element_text(hjust = 0.5)) + 
  geom_label(vjust=-0.5,hjust=0.25,fill="white") +
  labs(caption="Note marginal effects relative to 
       white respondents. \n* p < 0.1; ** p < 0.05; *** p < 0.01") + 
  facet_wrap(~model) + scale_shape_manual("Trust Effects",values=c(23,22,21))
ggsave(file="latent_scientific_trust_model.png", plot, width = 8, height = 5.43, units = "in")

mes <- subset(mes,!(mes$factor %in% c("region_factorWest","region_factorSouth","region_factorMidwest")))

plot <- ggplot(mes,aes(x=factor,y=AME,factor=factor,group=factor,label=label)) + 
  facet_wrap(~model) + coord_flip() + 
  geom_linerange(aes(x= factor, ymin = ylo90, ymax = yhi90), 
                 position = position_dodge(width=0.75), lwd  = 1) + 
  geom_pointrange(aes(x= factor, ymin = lower, ymax = upper), lwd = 1/2, 
                  position = position_dodge(width=0.75),fill="white",shape=21) + 
  theme_minimal() + scale_x_discrete("",labels=c("Age","Education","Female",
                                                 "Income","Liberal Ideology",
                                                 "Democrat","Independent",
                                                 "Asian Respondent","Black Respondent",
                                                 "Hispanic Respondent")) + 
  scale_y_continuous("Marginal Effect of Covariates on Latent Scientific Trust")  +
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
  labs(color="Trust Effects",shape="Trust Effects") + theme(legend.position = "none") + 
  theme(axis.text.x = element_text(hjust = 0.5),axis.text.y = element_text(hjust = 0.5)) + 
  geom_label(vjust=-0.5,hjust=0.25,fill="white") + 
  labs(caption="Note marginal effects for respondent race & 
       partisanship relative to baseline factor categories. Contextual 
       regions omitted. \nFactor Baselines: white respondents, Republican 
       identifiers. * p < 0.1; ** p < 0.05; *** p < 0.01") + facet_wrap(~model) 
ggsave(file="latent_scientific_trust_model_full.png", plot, width = 8, height = 5.43, units = "in")
```



