---
title: "Extension_FINAL"
author: "Solome Haile"
date: "2023-04-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readstata13)
library(ggplot2)
library(reshape2)
library(plyr)
library(margins)
library(descr)
library(sandwich)
library(pscl)
library(psych)
library(effects)
library(multiwayvcov)
library(mirt)
library(moments)
library(haven)
library(datawizard)
library(tidyverse)
library(labelled)
#setting working directory (Beza-- be sure to comments this out and set your own when you are coding!)
knitr::opts_knit$set(root.dir = "/Users/solomonaberash/Desktop/Graduate School/SP23 STATS/Rep Paper/BS-rep")

#Beza's working directory 
#knitr::opts_knit$set(root.dir = "/Users/bezataddess/Dropbox (Princeton)/Beza$SolomeReplication/Replication.stats")

```


```{r}
# load the foreign package to read wa
library(foreign)
# read in the .sav file using read.spss()
dataw46 <- read.spss("ATP W46.sav", to.data.frame = TRUE)
# view the first few rows of your data
head(dataw46)

```

```{r}
#Subsetting the variables we need for religion 
colnames(dataw46)
dataw46_subset <- subset(dataw46,
                      select=c(QKEY,CHURCHUNITE_W46,RELIGTRUST_W46,F_RACETHN,
                               F_RACECMB, CONFCLERGY1a_W46,CONFCLERGY1b_W46,
                               CONFCLERGY1c_W46,CONFCLERGY2a_W46,CONFCLERGY2b_W46,
                               CONFCLERGY2e_W46,CONFCLERGY2f_W46,
                            RELIG_INFL2_W46,ETERNAL_W46,CLERGY_RELIG_W46,
                            RELIG_FRIENDLYa_W46,RELIG_FRIENDLYb_W46,
                            RELIG_FRIENDLYc_W46,RELIG_FRIENDLYd_W46,
                            RELIG_FRIENDLYe_W46,RELIG_FRIENDLYf_W46,
                            FRIENDS_W46,F_METRO,F_CREGION,F_SEX,F_AGECAT,
                            F_EDUCCAT2,F_MARITAL,F_INCOME,F_CREGION,F_HISP,
                            F_RACECMB,F_NATIVITY,F_CITIZEN,F_RELIG,
                            F_PARTY_FINAL,F_PARTYSUM_FINAL,F_BORN,
                            F_ATTEND,F_IDEO,F_INCOME,F_INCOME_RECODE, 
                            F_E3,WEIGHT_W46))
head(dataw46_subset)
str(dataw46_subset)

# remove rows with missing values
dataw46_subset_complete <- na.omit(dataw46_subset)

# view the first few rows of the cleaned data frame (this might be a problem
#because the number of obs. went from 6364 to 2597; we might have to impute)
#imputing  for missing data: Amelia 
head(dataw46_subset_complete)

```
#Data Wrangleing: Religiousness Measure 

```{r}

#Religiousness as religious affiliation (combine 11 and 12)
levels(dataw46_subset$F_RELIG)
library(dplyr)

dataw46_subset <- dataw46_subset %>%
  mutate(affiliation = case_when(
    F_RELIG == "Protestant (for example, Baptist, Methodist, 
    Non-denominational, Lutheran, Presbyterian, Pentecostal,
    Episcopalian, Refo" ~ 1,
    F_RELIG == "Roman Catholic" ~ 2,
    F_RELIG == "Mormon (Church of Jesus Christ of
    Latter-day Saints or LDS)" ~ 3,
    F_RELIG == "Orthodox (such as Greek, Russian, 
    or some other Orthodox church)" ~ 4,
    F_RELIG == "Jewish" ~ 5,
    F_RELIG == "Muslim" ~ 6,
    F_RELIG == "Buddhist" ~ 7,
    F_RELIG == "Hindu" ~ 8,
    F_RELIG == "Atheist" ~ 9,
    F_RELIG == "Agnostic" ~ 10,
    F_RELIG == "Something else, Specify" ~ 11,
    F_RELIG == "Nothing in particular" ~ 12,
    F_RELIG == "Refused" ~ 13,
    TRUE ~ NA_integer_
  )) 
  
#Religiousness as religious attendance (seldom and a few times a year) 1 and 2: 
#often, 3: sometime 4 and 5: rarely and never : 6 and refused (as missing)
levels(dataw46_subset$F_ATTEND)

dataw46_subset <- dataw46_subset %>%
  mutate(attendance = case_when(
    F_ATTEND %in% c("More than once a week", "Once a week") ~ "often",
    F_ATTEND %in% c("Once or twice a month", "A few times a year",
                    "Seldom") ~ "sometimes",
    F_ATTEND %in% c("Never", "Refused") ~ "never",
    TRUE ~ F_ATTEND
  )) %>%
  mutate(attendance = factor(attendance, levels = c("never", 
                                                    "rarely", 
                                                    "sometimes", 
                                                    "often")))
dataw46_subset$attendance <- as.numeric(factor(dataw46_subset$attendance, 
                                               levels = c("never", "rarely", 
                                                          "sometimes",
                                                          "often")))


#Religiousness as religious as belief as relational  
levels(dataw46_subset$ETERNAL_W46)
dataw46_subset$eternal_life <- ifelse(dataw46_subset$ETERNAL_W46 == "My religion
                                      is the one true faith leading 
                                      to eternal life", 1,
                                      ifelse(dataw46_subset$ETERNAL_W46 == "Many
                                             religions can lead to eternal
                                             life", 2,
                                   ifelse(is.na(dataw46_subset$ETERNAL_W46) | 
                          dataw46_subset$ETERNAL_W46 == "Refused", NA, NA)))

#Religiousness as religious as  belief as shaping your way of life 
#(interpersonal life and world)
levels(dataw46_subset$CONFCLERGY1a_W46)
levels(dataw46_subset$CONFCLERGY1b_W46)
levels(dataw46_subset$CONFCLERGY1c_W46)
levels(dataw46_subset$CONFCLERGY2a_W46)
levels(dataw46_subset$CONFCLERGY2b_W46)
levels(dataw46_subset$CONFCLERGY2e_W46)
levels(dataw46_subset$CONFCLERGY2f_W46)


dataw46_subset <- dataw46 %>%
  mutate(CONFCLERGY1a_W46 = recode(CONFCLERGY1a_W46, 
                                   "A lot of confidence" = 4,
                                   "Some confidence" = 3,
                                   "Not much confidence" = 2,
                                   "No confidence at all" = 1),
         
         CONFCLERGY1b_W46 = recode(CONFCLERGY1b_W46, 
                                   "A lot of confidence" = 4,
                                   "Some confidence" = 3,
                                   "Not much confidence" = 2,
                                   "No confidence at all" = 1),
         
         CONFCLERGY1c_W46 = recode(CONFCLERGY1c_W46, 
                                   "A lot of confidence" = 4,
                                   "Some confidence" = 3,
                                   "Not much confidence" = 2,
                                   "No confidence at all" = 1),
         
         CONFCLERGY2a_W46 = recode(CONFCLERGY2a_W46, 
                                   "A lot of confidence" = 4,
                                   "Some confidence" = 3,
                                   "Not much confidence" = 2,
                                   "No confidence at all" = 1),
         
         CONFCLERGY2b_W46 = recode(CONFCLERGY2b_W46, 
                                   "A lot of confidence" = 4,
                                   "Some confidence" = 3,
                                   "Not much confidence" = 2,
                                   "No confidence at all" = 1),
         
         CONFCLERGY2e_W46 = recode(CONFCLERGY2e_W46, 
                                   "A lot of confidence" = 4,
                                   "Some confidence" = 3,
                                   "Not much confidence" = 2,
                                   "No confidence at all" = 1),
         
         CONFCLERGY2f_W46 = recode(CONFCLERGY2f_W46, 
                                   "A lot of confidence" = 4,
                                   "Some confidence" = 3,
                                   "Not much confidence" = 2,
                                   "No confidence at all" = 1
                                  ))


```

#Support for Covid policy scale

```{r}
 #Load Pew data from file
library(readstata13)
dataw64 <- read.dta13("ATP_W64.dta")

# Subset data to select specific variables of interest
dataw64_subset <- subset(dataw64, select = c(QKEY, COVID_COMFORT_a_W64,
                                             F_RACETHN,F_CREGION,
                                         COVID_COMFORT_b_W64,
                                         COVID_COMFORT_c_W64,
                                         COVID_COMFORT_d_W64,
                                         COVID_COMFORT_e_W64,
                                         COVID_RESTRICTION_a_W64,
                                         COVID_RESTRICTION_b_W64, 
                                         COVID_RESTRICTION_c_W64, 
                                         COVID_RESTRICTION_d_W64,
                                         COVID_RESTRICTION_e_W64,
                                         COVID_RESTRICTION_f_W64,
                                         COVID_RESTRICTION_g_W64,
                                          WEIGHT_W64))

# Create new object with COVID-19 restriction and ideological belief variables
covid_ideo_scales <- subset(dataw64_subset, select = c(QKEY, 
                                                       COVID_RESTRICTION_a_W64, 
                                                       COVID_RESTRICTION_b_W64, 
                                                       COVID_RESTRICTION_c_W64,
                                                       COVID_RESTRICTION_d_W64, 
                                                       COVID_RESTRICTION_e_W64, 
                                                       COVID_RESTRICTION_f_W64,
                                                       COVID_RESTRICTION_g_W64))
colnames(covid_ideo_scales) <- c("QKEY", 
                                 "restriction_intl_travel", 
                                 "restriction_most_business",
                                 "restriction_large_gatherings", 
                                 "restriction_sporting_events", 
                                 "restriction_closing_k12",
                                 "restriction_carry_out_only",
                                 "restriction_postponing_primary")

# Convert values in certain columns to numeric
for (i in 2:ncol(covid_ideo_scales)) {
  covid_ideo_scales[,i] <- as.character(covid_ideo_scales[,i])
}
covid_ideo_scales[covid_ideo_scales == "Necessary"] <- 1
covid_ideo_scales[covid_ideo_scales == "Unnecessary"] <- 0

```
# Trust variable contraction 

```{r}
# Load the data and subset the variables to create different kind of trust
library(readstata13)
library(ggplot2)
library(reshape2)
library(plyr)
library(margins)
library(descr)
library(sandwich)
library(pscl)
library(psych)
library(effects)
library(multiwayvcov)
library(mirt)
library(moments)
library(haven)
library(datawizard)
library(tidyverse)
library(labelled)

trust <- read.dta13("ATP_W42.dta")
trust <- subset(trust,select=c("QKEY","CONFa_W42","CONFb_W42","CONFd_F1_W42","CONFd_F2_W42", "POLICY1_W42","POLICY2_W42","POLICY3_W42","SCM2_W42","SCM3_W42","SCM4a_W42","SCM4b_W42"))

colnames(trust) <- c("QKEY","trust_elected_officials","trust_media","trust_medial_scientists","trust_scientists","scientists_active_role_policy","scientists_pivotal_policy","scientists_better_policy","scientific_method","scientists_judgement_facts","research_essential_immediate_applications","research_essential_advance_knowledge")

trust[trust == "Refused"] <- NA

for(i in 2:ncol(trust)){
  print(table(trust[,i]))
  print(levels(trust[,i]))
}
for(i in 2:ncol(trust)){
  trust[,i] <- as.character(trust[,i])
  print(table(trust[,i]))
}  
trust[trust == "Essential"] <- 4
trust[trust == "Important, but not essential"] <- 3
trust[trust == "Not too important"] <- 2
trust[trust == "Not important at all"] <- 1

trust[trust == "A great deal of confidence"] <- 4
trust[trust == "A fair amount of confidence"] <- 3
trust[trust == "Not too much confidence"] <- 2
trust[trust == "No confidence at all"] <- 1

trust[trust == "Scientists should take an active role in public policy debates about scientific issues"] <- 2
trust[trust == "Scientists should focus on establishing sound scientific facts and stay out of public policy debates"] <- 1

trust[trust == "Public opinion should NOT play an important role to guide policy decisions about scientific issues because these issues"] <- 2
trust[trust == "Public opinion should play an important role to guide policy decisions about scientific issues"] <- 1

trust[trust == "Usually BETTER at making good policy decisions about scientific issues than other people"] <- 3
trust[trust == "NEITHER BETTER NOR WORSE at making good policy decisions about scientific issues than other people"] <- 2
trust[trust == "Usually WORSE at making good policy decisions about scientific issues than other people"] <- 1

trust[trust == "The scientific method generally produces accurate conclusions"] <- 2
trust[trust == "The scientific method can be used to produce any conclusion the researcher wants"] <- 1

trust[trust == "Scientists make judgments based solely on the facts"] <- 2
trust[trust == "Scientists' judgments are just as likely to be biased as other people's"] <- 1

trust$trust_scientists <- ifelse(is.na(trust$trust_medial_scientists),trust$trust_scientists,ifelse(is.na(trust$trust_scientists),trust$trust_medial_scientists,NA))

trust$trust_medial_scientists <- NULL
trust$scientists_pivotal_policy <- NULL

for(i in 2:ncol(trust)){
  trust[,i] <- as.numeric(trust[,i])
  print(table(trust[,i]))
}  

factanal <- fa(trust[,c(4:10)], nfactors=2, rotate="promax", fm="pa")
scores <- data.frame(factanal$scores)
loadings(factanal)
loadings <- factanal$loadings
loadings <- data.frame(f1 = loadings[,1],f2=loadings[,2])

plot(factanal$loadings,type="n") # set up plot 
text(factanal$loadings,labels=names(trust)[4:10],cex=.7) # add variable names

library(ggrepel)

alpha(trust[,c(4:8)])
skewness(loadings$f1, na.rm=T)
kurtosis(loadings$f1, na.rm=T)

alpha(trust[,c(9:10)])
skewness(loadings$f2, na.rm=T)
kurtosis(loadings$f2, na.rm=T)

loadings$vars <- ifelse(rownames(loadings) %in% "trust_scientists","Trust Scientists",ifelse(rownames(loadings) %in% "scientists_active_role_policy","Scientists Active Role Policy",ifelse(rownames(loadings) %in% "scientists_pivotal_policy","PO Guiding Policy Science",ifelse(rownames(loadings) %in% "scientists_better_policy","Scientists Better Policymakers",ifelse(rownames(loadings) %in% "scientific_method","Scientific Method Validity",ifelse(rownames(loadings) %in% "scientists_judgement_facts","Unbiased Scientists",ifelse(rownames(loadings) %in% "research_essential_immediate_applications","Research Essential Applications",ifelse(rownames(loadings) %in% "research_essential_advance_knowledge","Research Essential Knowledge",NA))))))))

# plot <- ggplot(loadings,aes(x = f1, y=f2,label=vars)) + theme_minimal() + geom_label_repel() + scale_x_continuous("First Dimension Factor") + scale_y_continuous("Second Dimension Factor") + geom_segment(aes(x = 0,y = 0,xend = f1,yend = f2),arrow=arrow())  # (Proportion of Variance F1: 18%) (Propoportion of F2 Variance 16%)" 
# 
# grid.newpage()
# footnote <- expression("Cronbach's Standardized"~alpha~"="~0.66)
# g <- arrangeGrob(plot, bottom = textGrob(footnote, x = 0.025, hjust = 0, vjust= 0, y=0.75, gp = gpar(fontface = "italic", fontsize = 9, col = "black")))
# grid.draw(g)
# #ggsave(file="factor_analysis_scientific_trust.png", g, width = 8, height = 5.43, units = "in")

trust <- cbind(trust,scores)
colnames(trust)[11:12] <- c("trust_scientists_fa_dim1","trust_scientists_fa_dim2")

```
#Covariates: 

```{r}
library(tidyverse)
#Transforming gender covariate 
dataw46_subset$female <- as.character(dataw46_subset$F_SEX)
dataw46_subset$female <- recode(dataw46_subset$female, "1" = "Male", "2"= "Female")
dataw46_subset$female <- factor(dataw46_subset$female, levels=c("Male","Female"))

#Transforming & cleaning age covariate
dataw46_subset$age_linear <- as.factor(factor(dataw46_subset$F_AGECAT))
dataw46_subset$age_linear[dataw46_subset$age_linear %in% 5] <- NA # Get rid of refused

#transforming & cleaning education covariate
dataw46_subset$educ_linear <- as.factor(factor(dataw46_subset$F_EDUCCAT2))
dataw46_subset$educ_linear[dataw46_subset$educ_linear %in% 7] <- NA # Get rid of refused

#transforming & cleaning marital covariate
dataw46_subset$marital_status <- ifelse(dataw46_subset$F_MARITAL %in% "Married",1,0)
dataw46_subset$marital_status[dataw46_subset$F_MARITAL %in% "Refused"] <- NA # Get rid of refused

#transforming & cleaning income covariate
dataw46_subset$income_linear <- as.factor(factor(dataw46_subset$F_INCOME))
dataw46_subset$income_linear[dataw46_subset$income_linear %in% 10] <- NA # Get rid of refused

#transforming & cleaning region & white race covariates
library(dplyr)

dataw46_subset <- dataw46_subset %>% 
  mutate(region_factor = F_CREGION,
         white_respondent = case_when(F_RACETHN == "White non-Hispanic" ~ 1,
                                      F_RACETHN != "White non-Hispanic" ~ 0,
                                      TRUE ~ NA_real_)
        )

#getting other race covariate and merging with the dataw46_subset data 
library(haven)
dataw42 <- read_dta("ATP_W42.dta")
dataw42_sub <- dataw42[,c("QKEY", "F_RACECMB")]

dim(dataw46_subset)
dim(dataw42)

dataw46_subset <- merge(dataw46_subset, dataw42_sub, 
                        by = "QKEY",
                        all = TRUE, suffixes = c("_w46", "_w42"))

dataw46_subset$dataw42_sub <- ifelse(dataw46_subset$F_RACETHN %in% "White non-Hispanic","white",ifelse(dataw46_subset$F_RACETHN %in% "Black non-Hispanic",
                                                                                                       "black",ifelse(dataw46_subset$F_RACETHN %in% "Hispanic","hispanic",NA)))
dataw46_subset$dataw42_sub <- ifelse(is.na(dataw46_subset$dataw42_sub) & dataw46_subset$F_RACECMB %in% "Asian or Asian-American","asian",dataw46_subset$dataw42_sub)

dataw46_subset$dataw42_sub <- factor(dataw46_subset$dataw42_sub,levels=c("white","black","hispanic","asian"))

```

#Run first pass of analysis 

```{r}
#Linear model: religion as affiliation on scientific trust 
relig_trust <- lm(affiliation ~ trust_scientists_fa_dim1 + 
                    marital_status + income_linear + 
                    educ_linear + age_linear + female,
          data = dataw64_subset)

#Linear model: religion as eternal_life on scientific trust 
relig_trust <- lm(eternal_life ~ trust_scientists_fa_dim1 + 
                    marital_status + income_linear + 
                    educ_linear + age_linear + female,
          data = dataw64_subset)

#Linear model: religion as attendance on scientific trust 
relig_trust <- lm(attendance ~ trust_scientists_fa_dim1 + 
                    marital_status + income_linear + 
                    educ_linear + age_linear + female,
          data = dataw64_subset)

#Linear model: religion as CONFCLERGY1a_W46 on scientific trust 
relig_trust <- lm(CONFCLERGY1a_W46 ~ trust_scientists_fa_dim1 + 
                    marital_status + income_linear + 
                    educ_linear + age_linear + female,
          data = dataw64_subset)
```

#Adding Trust in Religious Institutions

# Data Analysis: COVID Policy ~ Scientific Trust: Baseline Effects

## Baseline Trust Effects
```{r, warning=FALSE}
baseline_trust_effects <- list()
for(i in which(colnames(pew) == "restriction_intl_travel"):
    which(colnames(pew) == "restriction_postponing_primary")){
  summary(model <- glm(pew[,i] ~ trust_scientists_fa_dim1 + 
                         trust_media + trust_elected_officials + female +
                         pid3 + libcon + age_linear + educ_linear + 
                         income_linear + race3 + region_factor, 
                       data=pew, weights=weight, family = binomial(link = "logit")))
  mes <- summary(margins(model, 
                         variables=c("trust_scientists_fa_dim1","trust_media",
                                     "trust_elected_officials"),
                         type="response", change="minmax"))
  mes$model <- colnames(pew)[i]
  mes$category <- "Full Sample Baseline"
  baseline_trust_effects[[i]] <- mes
}
baseline_trust_effects <- ldply(baseline_trust_effects,data.frame)

baseline_trust_effects$pid3 <- "Full Baseline Sample"
baseline_trust_effects$category <- NULL

effects <- baseline_trust_effects
effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))
effects$model2 <- ifelse(effects$model %in% "restriction_carry_out_only",
                         "Dependent Variable: Restaurants Carry Out Only",
                  ifelse(effects$model %in% "restriction_closing_k12",
                         "Dependent Variable: Close K-12 Schools",
                  ifelse(effects$model %in% "restriction_intl_travel",
                         "Dependent Variable: Restrict International Travel",
                  ifelse(effects$model %in% "restriction_large_gatherings",
                         "Dependent Variable: Restrict Large Gatherings",
                  ifelse(effects$model %in% "restriction_most_business",
                         "Dependent Variable: Restrict Most Businesses",
                  ifelse(effects$model %in% "restriction_postponing_primary",
                         "Dependent Variable: Postpone Primary Elections",
                  ifelse(effects$model %in% "restriction_sporting_events",
                         "Dependent Variable: Restrict Sporting Events",NA)))))))

effects$factor <- ifelse(effects$factor %in% "trust_elected_officials","Elected Officials Trust",
                  ifelse(effects$factor %in% "trust_media","Media Trust",
                  ifelse(effects$factor %in% "trust_scientists_fa_dim1","Scientific Trust",NA)))

effects$label <- ifelse(effects$p < 0.01,paste(round(effects$AME,2),"***",sep=""),
                  ifelse(effects$p < 0.05,paste(round(effects$AME,2),"**",sep=""),
                  ifelse(effects$p < 0.10,paste(round(effects$AME,2),"*",sep=""),NA)))

for(i in unique(effects$model)){
  x <- subset(effects,effects$model %in% i)
  plot <- ggplot(x,aes(x=factor,y=AME,factor=factor,group=factor,color=factor,
                       shape=factor,label=label,fill=factor)) + 
    facet_wrap(~model2) + coord_flip() + 
    geom_linerange(aes(x= factor, ymin = ylo90, ymax = yhi90), 
                   position = position_dodge(width=0.75), lwd  = 1) + 
    geom_pointrange(aes(x= factor, ymin = lower, ymax = upper), lwd = 1/2, 
                    position = position_dodge(width=0.75),fill="white") + 
    theme_minimal() + scale_x_discrete("") + 
    scale_y_continuous("Min/Max First Difference Marginal Effects on 
                       Pr(Necessary Government Policy)") + 
    geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  
    labs(color="Trust Effects",shape="Trust Effects") + 
    theme(legend.position = "none") + 
    theme(axis.text.x = element_text(hjust = 0.5),
          axis.text.y = element_text(hjust = 0.5)) + 
    geom_label(vjust=-0.5,hjust=0.25,fill="white") + 
    labs(caption="* p < 0.1; ** p < 0.05; *** p < 0.01") + 
    scale_shape_manual("",values=c(23,22,21))
  print(plot)
  #ggsave(file=paste(i,"_model",".png",sep=""), plot, width = 8, height = 5.43, units = "in")
}
```



# Data Analysis Figures: OLS Composite Models
```{r, warning=FALSE}
model <- glm(covid_restriction_irt ~ trust_scientists_fa_dim1 + 
                       trust_media + trust_elected_officials + 
                       female + libcon + age_linear + educ_linear + 
                       income_linear + race3 + region_factor, 
                     data=pew, weights=weight, family = gaussian(identity))

baseline_trust_effects.2 <- summary(margins(model, 
                                            variables=c("trust_scientists_fa_dim1",
                                                        "trust_media","trust_elected_officials"), 
                                            type="response", change="minmax"))
baseline_trust_effects.2$model <- "DV: Latent Policy Scale"
baseline_trust_effects.2$pid3 <- "Full Sample"

effects <- baseline_trust_effects.2
effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))
effects$ame_label <- round(effects$AME,2)
effects$factor <- ifelse(effects$factor %in% "trust_elected_officials",
                         "Elected Officials Trust",
                  ifelse(effects$factor %in% "trust_media",
                         "Media Trust",
                  ifelse(effects$factor %in% "trust_scientists_fa_dim1",
                         "Scientific Trust",NA)))
effects$label <- ifelse(effects$p < 0.01,paste(round(effects$AME,2),"***",sep=""),
                  ifelse(effects$p < 0.05,paste(round(effects$AME,2),"**",sep=""),
                  ifelse(effects$p < 0.10,paste(round(effects$AME,2),"*",sep=""),NA)))

plot <- ggplot(effects,aes(x=factor,y=AME,factor=factor,
                           group=factor,color=factor,shape=factor,label=label,fill=factor)) + 
  facet_wrap(~model) + coord_flip() + 
  geom_linerange(aes(x= factor, ymin = ylo90, ymax = yhi90), 
                 position = position_dodge(width=0.75), lwd  = 1) + 
  geom_pointrange(aes(x= factor, ymin = lower, ymax = upper), lwd = 1/2, 
                  position = position_dodge(width=0.75),fill="white") + 
  theme_minimal() + scale_x_discrete("") + 
  scale_y_continuous("Min/Max First Difference Marginal Effects on 
                     Latent Necessary Government Policies")  + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  
  labs(color="Trust Effects",shape="Trust Effects") + 
  theme(legend.position = "none") + 
  theme(axis.text.x = element_text(hjust = 0.5),axis.text.y = element_text(hjust = 0.5)) + 
  geom_label(vjust=-0.5,hjust=0.25,fill="white") + 
  labs(caption="* p < 0.1; ** p < 0.05; *** p < 0.01") + 
  scale_shape_manual("",values=c(23,22,21))
#ggsave(file="latent_policy_scale_model.png", plot, width = 8, height = 5.43, units = "in")

model <- glm(summated_restriction_scale ~ trust_scientists_fa_dim1 + 
                       trust_media + trust_elected_officials + female + 
                       libcon + age_linear + educ_linear + income_linear + 
                       race3 + region_factor, data=pew, weights=weight, 
                     family = "poisson")
baseline_trust_effects.3 <- summary(margins(model, 
                                            variables=c("trust_scientists_fa_dim1",
                                                        "trust_media","trust_elected_officials"),
                                            type="response", change="minmax"))
baseline_trust_effects.3$model <- "DV: Summated Policy Scale"
baseline_trust_effects.3$pid3 <- "Full Sample"

effects <- baseline_trust_effects.3
effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))
effects$ame_label <- round(effects$AME,2)
effects$factor <- ifelse(effects$factor %in% "trust_elected_officials",
                         "Elected Officials Trust",
                  ifelse(effects$factor %in% "trust_media","Media Trust",
                  ifelse(effects$factor %in% "trust_scientists_fa_dim1",
                         "Scientific Trust",NA)))
effects$label <- ifelse(effects$p < 0.01,paste(round(effects$AME,2),"***",sep=""),
                ifelse(effects$p < 0.05,paste(round(effects$AME,2),"**",sep=""),
                  ifelse(effects$p < 0.10,paste(round(effects$AME,2),"*",sep=""),NA)))

plot <- ggplot(effects,aes(x=factor,y=AME,
                           factor=factor,group=factor,
                           color=factor,shape=factor,label=label)) + 
  facet_wrap(~model) + coord_flip() +
  geom_linerange(aes(x= factor, ymin = ylo90, ymax = yhi90), 
                 position = position_dodge(width=0.75), lwd  = 1) + 
  geom_pointrange(aes(x= factor, ymin = lower, ymax = upper), lwd = 1/2, 
                  position = position_dodge(width=0.75),fill="white") + 
  theme_minimal() + scale_x_discrete("") + 
  scale_y_continuous("Min/Max First Difference Marginal Effects on 
                     Number of Necessary Government Policies")  + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  
  labs(color="Trust Effects",shape="Trust Effects") + theme(legend.position = "none") +
  theme(axis.text.x = element_text(hjust = 0.5),
        axis.text.y = element_text(hjust = 0.5)) + 
  geom_label(vjust=-0.5,hjust=0.25,fill="white") + 
  labs(caption="* p < 0.1; ** p < 0.05; *** p < 0.01") + 
  scale_shape_manual("",values=c(23,22,21))
print(plot)
#ggsave(file="summated_policy_scale_model.png", plot, width = 8, height = 5.43, units = "in")
```

# Distribution of Summated Rating Scales
```{r, warning=FALSE}
x <- subset(pew,select=c(summated_restriction_scale,trust_scientists_fa_dim1,pid3,trust_media,trust_elected_officials,female,libcon,age_linear,educ_linear,income_linear,white_respondent,region_factor,race3))
x1 <- na.omit(x)
x <- na.omit(x)
x1$race3 <- "Full Sample"

x <- subset(x,select=c(summated_restriction_scale,race3))
x$n <- 1
xs <- ddply(x,.(summated_restriction_scale,race3),summarise,total=sum(n,na.rm=T))
x <- ddply(x,.(race3),summarise,total_race3=sum(n,na.rm=T))
xs <- merge(xs,x,by=c("race3"))
xs$prop <- xs$total/xs$total_race3

x1 <- subset(x1,select=c(summated_restriction_scale,race3))
x1$n <- 1
xs1 <- ddply(x1,.(summated_restriction_scale),summarise,total=sum(n,na.rm=T))
xs1$total_race3 <- sum(x1$n,na.rm=T)
xs1$prop <- xs1$total/xs1$total_race3
xs1$race3 <- "Full Sample"

x <- rbind(xs,xs1)
x$race3 <- factor(x$race3,
                  levels=c("asian","black","hispanic","white","Full Sample"),
                  labels=c("Asian Respondents","Black Respondents",
                           "Hispanic Respondents","White Respondents","Full Sample"))

plot <- ggplot(x, aes(x=factor(summated_restriction_scale), 
                      y=prop, label=round(prop,2))) + 
  geom_point(stat='identity', size=6*1.25) + 
  geom_segment(aes(y=0,x=factor(summated_restriction_scale),
                   yend=prop,xend=factor(summated_restriction_scale)))+ 
  geom_text(color="white", size=2*1.25) + coord_flip() + 
  facet_wrap(~race3) + theme_minimal() + theme(legend.position = "none") + 
  scale_x_discrete("Number of Restrictive COVID-19 Policies Necessary") + 
  scale_y_continuous("Proportion of Respondents")
#ggsave(file="number_policies_dotplot.png", plot, width = 8, height = 5.43, units = "in")
```

# Conditioned by Race | Data Analysis: COVID Policy ~ Scientific Trust: Baseline Effects [W/ TRUST IN RELIGIOUS INSTITUTIONS]

## Baseline Trust Effects
```{r, warning=FALSE}
baseline_trust_effects.race <- list()
for(i in which(colnames(pew) == "restriction_intl_travel"):
    which(colnames(pew) == "restriction_postponing_primary")){
  summary(model <- glm(pew[,i] ~ trust_scientists_fa_dim1*race3 + 
                         trust_media + trust_elected_officials + 
                         female + pid3 + libcon + age_linear + 
                         educ_linear + income_linear + 
                         region_factor, data=pew, weights=weight, 
                       family = binomial(link = "logit")))
  mes <- summary(margins(model, 
                         variables=c("trust_scientists_fa_dim1","trust_media",
                                     "trust_elected_officials"),
                         at=list(race3=c("asian","black","white","hispanic")), 
                         type="response", change="minmax",))
  mes$model <- colnames(pew)[i]
  mes$category <- "Full Sample Baseline"
  baseline_trust_effects.race[[i]] <- mes
}
baseline_trust_effects.race <- ldply(baseline_trust_effects.race,data.frame)


effects <- baseline_trust_effects.race
effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))
effects$model2 <- ifelse(effects$model %in% "restriction_carry_out_only",
                         "Dependent Variable: Restaurants Carry Out Only",
                  ifelse(effects$model %in% "restriction_closing_k12",
                         "Dependent Variable: Close K-12 Schools",
                  ifelse(effects$model %in% "restriction_intl_travel",
                         "Dependent Variable: Restrict International Travel",
                  ifelse(effects$model %in% "restriction_large_gatherings",
                         "Dependent Variable: Restrict Large Gatherings",
                  ifelse(effects$model %in% "restriction_most_business",
                         "Dependent Variable: Restrict Most Businesses",
                  ifelse(effects$model %in% "restriction_postponing_primary",
                         "Dependent Variable: Postpone Primary Elections",
                  ifelse(effects$model %in% "restriction_sporting_events",
                         "Dependent Variable: Restrict Sporting Events",NA)))))))
effects$factor <- ifelse(effects$factor %in% "trust_elected_officials",
                         "Elected Officials Trust",
                  ifelse(effects$factor %in% "trust_media","Media Trust",
                  ifelse(effects$factor %in% "trust_scientists_fa_dim1",
                         "Scientific Trust",NA)))
effects$race3 <- factor(effects$race3,levels=c("asian","black","white","hispanic"), 
                        labels=c("Asian Respondents","Black Respondents",
                                 "White Respondents","Hispanic Respondents"))

for(i in unique(effects$model)){
  x <- subset(effects,effects$model %in% i)
  plot <- ggplot(x,aes(x=race3,y=AME,factor=factor,group=factor,
                       color=factor,shape=factor)) +
    facet_wrap(~model2) + coord_flip() + 
    geom_linerange(aes(x= race3, ymin = ylo90, ymax = yhi90), 
                   position = position_dodge(width=0.75), lwd  = 1) + 
    geom_pointrange(aes(x= race3, ymin = lower, ymax = upper), lwd = 1/2, 
                    position = position_dodge(width=0.75),fill="white") + 
    theme_minimal() + scale_x_discrete("") + 
    scale_y_continuous("Min/Max First Difference Marginal 
                       Effects on Pr(Necessary Government Policy)") + 
    geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
    labs(color="Trust Effects",shape="Trust Effects") + theme(legend.position = "bottom") + 
    theme(axis.text.x = element_text(hjust = 0.5),axis.text.y = element_text(hjust = 0.5)) + 
    scale_shape_manual("Trust Effects",values=c(23,22,21))
  print(plot)
  #ggsave(file=paste(i,"_race3_model",".png",sep=""), plot, width = 8, height = 5.43, units = "in")
}
```

# Data Analysis Figures: OLS Composite Models
```{r, warning=FALSE}
model <- glm(covid_restriction_irt ~ trust_scientists_fa_dim1*race3 + 
                       trust_media*race3 + trust_elected_officials*race3 + 
                       female + libcon + age_linear + educ_linear + 
                       income_linear + region_factor, data=pew, 
                     weights=weight, family = gaussian(identity))
baseline_trust_effects.4 <- summary(margins(model, 
                                            variables=c("trust_scientists_fa_dim1",
                                                        "trust_media","trust_elected_officials"),
                                            at=list(race3=c("asian","white","black","hispanic")), 
                                            type="response", change="minmax"))
baseline_trust_effects.4$model <- "DV: Latent Policy Scale"
baseline_trust_effects.4$pid3 <- "Full Sample"

effects <- baseline_trust_effects.4
effects$race3 <- factor(effects$race3,levels=c("asian","black","white","hispanic"), 
                        labels=c("Asian Respondents","Black Respondents",
                                 "White Respondents","Hispanic Respondents"))

effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))

effects$factor <- ifelse(effects$factor %in% "trust_elected_officials",
                         "Elected Officials Trust",
                  ifelse(effects$factor %in% "trust_media","Media Trust",
                  ifelse(effects$factor %in% "trust_scientists_fa_dim1",
                         "Scientific Trust",NA)))

plot <- ggplot(effects,aes(x=race3,y=AME,factor=factor,group=factor,color=factor,shape=factor)) + 
  facet_wrap(~model) + coord_flip() + 
  geom_linerange(aes(x= race3, ymin = ylo90, ymax = yhi90), 
                 position = position_dodge(width=0.75), lwd  = 1) + 
  geom_pointrange(aes(x= race3, ymin = lower, ymax = upper), lwd = 1/2, 
                  position = position_dodge(width=0.75),fill="white") + 
  theme_minimal() + scale_x_discrete("") + 
  scale_y_continuous("Min/Max First Difference Marginal Effects on 
                     Latent Policy Restriction Scale") + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  
  labs(color="Trust Effects",shape="Trust Effects") + 
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(hjust = 0.5),
        axis.text.y = element_text(hjust = 0.5)) + 
  scale_shape_manual("Trust Effects",values=c(23,22,21))
print(plot)
#ggsave(file="latent_policy_scale_race3_model.png", plot, width = 8, height = 5.43, units = "in")

model <- glm(summated_restriction_scale ~ trust_scientists_fa_dim1*race3 + 
                       trust_media*race3 + trust_elected_officials*race3 + 
                       female + libcon + age_linear + educ_linear + 
                       income_linear + region_factor, data=pew,
                     weights=weight, family = gaussian(identity))
baseline_trust_effects.5 <- summary(margins(model, 
                                            variables=c("trust_scientists_fa_dim1",
                                                        "trust_media",
                                                        "trust_elected_officials"),
                                            at=list(race3=c("asian","white","black",
                                                            "hispanic")), 
                                            type="response", change="minmax"))
baseline_trust_effects.5$model <- "DV: Summated Policy Scale"
baseline_trust_effects.5$pid3 <- "Full Sample"

effects <- baseline_trust_effects.5
effects$race3 <- factor(effects$race3,levels=c("asian","black","white","hispanic"), 
                        labels=c("Asian Respondents","Black Respondents",
                                 "White Respondents","Hispanic Respondents"))

effects$ylo90 <- (effects$AME - (qt(.95, 100) * effects$SE))
effects$yhi90 <- (effects$AME + (qt(.95, 100) * effects$SE))

effects$factor <- ifelse(effects$factor %in% "trust_elected_officials",
                         "Elected Officials Trust",
                  ifelse(effects$factor %in% "trust_media","Media Trust",
                  ifelse(effects$factor %in% "trust_scientists_fa_dim1",
                         "Scientific Trust",NA)))

plot <- ggplot(effects,aes(x=race3,y=AME,factor=factor,group=factor,color=factor,shape=factor)) + 
  facet_wrap(~model) + coord_flip() + 
  geom_linerange(aes(x= race3, ymin = ylo90, ymax = yhi90), 
                 position = position_dodge(width=0.75), lwd  = 1) + 
  geom_pointrange(aes(x= race3, ymin = lower, ymax = upper), lwd = 1/2, 
                  position = position_dodge(width=0.75),fill="white") + 
  theme_minimal() + scale_x_discrete("") + 
  scale_y_continuous("Min/Max First Difference Marginal Effects on 
                     Number of Necessary Government Policies") + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  
  labs(color="Trust Effects",shape="Trust Effects") + 
  theme(legend.position = "bottom") + theme(axis.text.x = element_text(hjust = 0.5),
                                            axis.text.y = element_text(hjust = 0.5)) + 
  scale_shape_manual("Trust Effects",values=c(23,22,21))
print(plot)
#ggsave(file="summated_policy_scale_race3_model.png", plot, width = 8, height = 5.43, units = "in")
```

# Boxplot by Race
```{r, warning=FALSE}
x <- subset(pew,select=c(race3,trust_scientists_fa_dim1))
x <- na.omit(x)
print(summary(aov(trust_scientists_fa_dim1 ~ race3, data = x)))
y <- subset(pew,select=c(race3,trust_scientists_fa_dim1))
y$race3 <- "Full Sample"
x <- rbind(x,y)

plot <- ggplot(x, aes(x=race3,y=trust_scientists_fa_dim1, group=race3,fill=race3)) + 
  geom_boxplot(alpha=0.2) + theme_minimal() + 
  scale_y_continuous("Latent Scientific Trust") + 
  scale_x_discrete("",labels=c("White Respondents","Black Respondents",
                               "Hispanic Respondents","Asian Respondents","Full Sample")) + 
  theme(legend.position = "none") + 
  labs(caption="ANOVA suggests significant differences in mean latent 
       scientific trust across racial groups, p < 0.01.") + 
  geom_jitter(aes(colour=race3),alpha=0.075) + 
  scale_color_manual("",values=c("#F8766D","#7CAE00","#00BFC4","#529EFF","gray")) + 
  scale_fill_manual("",values=c("#F8766D","#7CAE00","#00BFC4","#529EFF","gray"))
#ggsave(file="scientific_trust_boxplots_by_race3.png", plot, width = 8, height = 5.43, units = "in")
```

# Data Analysis Figures: OLS Composite Models 
```{r, warning=FALSE}
model <- lm(trust_scientists_fa_dim1 ~ female + pid3 + libcon + 
                      age_linear + educ_linear + income_linear + race3 + 
                      region_factor, data=pew, weights=weight)

mes <- summary(margins(model, type="response", change="minmax"))
mes$race3 <- factor(mes$factor,levels=c("race3asian","race3black","race3hispanic"),
                    labels=c("Asian Respondents","Black Respondents",
                             "Hispanic Respondents"))

mes$label <- ifelse(mes$p < 0.01,paste(round(mes$AME,2),"***",sep=""),
                    ifelse(mes$p < 0.05,paste(round(mes$AME,2),"**",sep=""),
                    ifelse(mes$p < 0.10,paste(round(mes$AME,2),"*",sep=""),NA)))

mes$ylo90 <- (mes$AME - (qt(.95, 100) * mes$SE))
mes$yhi90 <- (mes$AME + (qt(.95, 100) * mes$SE))
mes$model <- "DV: Latent Scientific Trust "

plot <- ggplot(subset(mes,!is.na(mes$race3)),
               aes(x=race3,y=AME,factor=race3,group=race3,
                   color=race3,shape=race3,label=label,fill=race3)) + 
  facet_wrap(~model) + coord_flip() + 
  geom_linerange(aes(x= race3, ymin = ylo90, ymax = yhi90), 
                 position = position_dodge(width=0.75), lwd  = 1) + 
  geom_pointrange(aes(x= race3, ymin = lower, ymax = upper), lwd = 1/2, 
                  position = position_dodge(width=0.75),fill="white") + 
  theme_minimal() + scale_x_discrete("") + 
  scale_y_continuous("Marginal Effect of Race on Latent Scientific Trust")  + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) +  
  labs(color="Trust Effects",shape="Trust Effects") + 
  theme(legend.position = "none") + 
  theme(axis.text.x = element_text(hjust = 0.5),axis.text.y = element_text(hjust = 0.5)) + 
  geom_label(vjust=-0.5,hjust=0.25,fill="white") +
  labs(caption="Note marginal effects relative to 
       white respondents. \n* p < 0.1; ** p < 0.05; *** p < 0.01") + 
  facet_wrap(~model) + scale_shape_manual("Trust Effects",values=c(23,22,21))
ggsave(file="latent_scientific_trust_model.png", plot, width = 8, height = 5.43, units = "in")

mes <- subset(mes,!(mes$factor %in% c("region_factorWest","region_factorSouth","region_factorMidwest")))

plot <- ggplot(mes,aes(x=factor,y=AME,factor=factor,group=factor,label=label)) + 
  facet_wrap(~model) + coord_flip() + 
  geom_linerange(aes(x= factor, ymin = ylo90, ymax = yhi90), 
                 position = position_dodge(width=0.75), lwd  = 1) + 
  geom_pointrange(aes(x= factor, ymin = lower, ymax = upper), lwd = 1/2, 
                  position = position_dodge(width=0.75),fill="white",shape=21) + 
  theme_minimal() + scale_x_discrete("",labels=c("Age","Education","Female",
                                                 "Income","Liberal Ideology",
                                                 "Democrat","Independent",
                                                 "Asian Respondent","Black Respondent",
                                                 "Hispanic Respondent")) + 
  scale_y_continuous("Marginal Effect of Covariates on Latent Scientific Trust")  +
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
  labs(color="Trust Effects",shape="Trust Effects") + theme(legend.position = "none") + 
  theme(axis.text.x = element_text(hjust = 0.5),axis.text.y = element_text(hjust = 0.5)) + 
  geom_label(vjust=-0.5,hjust=0.25,fill="white") + 
  labs(caption="Note marginal effects for respondent race & 
       partisanship relative to baseline factor categories. Contextual 
       regions omitted. \nFactor Baselines: white respondents, Republican 
       identifiers. * p < 0.1; ** p < 0.05; *** p < 0.01") + facet_wrap(~model) 
ggsave(file="latent_scientific_trust_model_full.png", plot, width = 8, height = 5.43, units = "in")
```



